\documentclass[11pt]{article}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{cmap}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage[left=1.2cm,top=1.4cm,right=1.2cm,bottom=1.2cm]{geometry}
\setlength{\parindent}{0pt}
\setlist[itemize]{leftmargin=*, noitemsep, topsep=2pt, partopsep=0pt, parsep=2pt, label={\textbf{-}}}

\begin{document}

\begin{center}
    {\LARGE \textbf{Kevin Bravo}}\\
    Product Engineer | Full-Stack Applications, Internal Tools, AI Workflows \\
    \hrulefill
\end{center}

\begin{center}
    \href{mailto:0bravokevin@gmail.com}{0bravokevin@gmail.com}
    \textbullet\
    \href{http://www.kevinbravo.com}{www.kevinbravo.com}
    \textbullet\
    Remote, Venezuela
\end{center}

\vspace{4pt}
\begin{center}
    \textbf{Professional Summary}
\end{center}
\vspace{-4pt}
Product Engineer and Software Engineer with 4+ years of experience building and shipping production web applications, internal platforms, dashboards, and workflow systems across startup, government, and nonprofit environments. Strong background in full-stack development, product ownership, data modeling, frontend and backend implementation, API integrations, and taking software from idea to launch. Built products for the U.S. Department of State's Venezuela Affairs Unit, Free2Z, AVAA, and independent initiatives, with consistent ownership of discovery, architecture, implementation, iteration, and delivery in fast-moving environments.

\vspace{8pt}
\begin{center}
    \textbf{Core Skills}
\end{center}
\vspace{-4pt}
\textbf{Languages and Frameworks:} TypeScript, JavaScript, Python, React, Next.js, SvelteKit, Django, HTML, CSS, Tailwind CSS \\
\textbf{Data and Backend:} PostgreSQL, SQL, REST APIs, data modeling, backend architecture, service integrations, reporting systems \\
\textbf{Product and Delivery:} product engineering, prototyping, internal tools, dashboard development, workflow automation, user-centered problem solving, cross-functional collaboration, zero-to-one product delivery \\
\textbf{AI and Automation:} AI tooling, agent systems, automation scripting, LLM-enabled workflows, AI-assisted product development \\
\textbf{Other:} Docker, Power BI, server-side rendering, real-time features, CMS tooling

\vspace{8pt}
\begin{center}
    \textbf{Experience}
\end{center}
\vspace{-4pt}

\textbf{Proyecto Educa} \hfill \textit{Remote, Venezuela} \\
\textbf{Chief Technology Officer} \hfill \textit{Dec 2025 -- Present}
\begin{itemize}
    \item Own product and technical direction for education-focused platforms, translating ambiguous stakeholder needs into product plans, system design, delivery priorities, and shipped software.
    \item Lead hands-on execution across architecture, frontend and backend implementation, testing, and release quality for digital products used in real operating workflows.
\end{itemize}

\vspace{10pt}
\textbf{Free2Z} \hfill \textit{Remote, Venezuela} \\
\textbf{Principal Software Engineer} \hfill \textit{Apr 2025 -- Apr 2026}
\begin{itemize}
    \item Led a production migration from React to SvelteKit, improving maintainability, frontend architecture, performance, and server-side rendering for a live product.
    \item Integrated frontend systems with Python and Django APIs, shipped live video features through Dyte, and built a CMS suite for content and product operations.
\end{itemize}

\vspace{10pt}
\textbf{U.S. Department of State (via AVAA)} \hfill \textit{Remote, Venezuela} \\
\textbf{Software Engineer | Full-Stack Developer} \hfill \textit{Nov 2024 -- Aug 2025}
\begin{itemize}
    \item Built Billingua Talent as the sole engineer, owning the full product lifecycle from requirements and relational data architecture to frontend and backend implementation, dashboards, and production delivery.
    \item Shipped candidate profiles, advisor dashboards, service-management workflows, registration flows, and reporting views that improved talent visibility, English-readiness planning, and operational follow-up across centers.
\end{itemize}

\vspace{10pt}
\textbf{Freelance} \hfill \textit{Remote} \\
\textbf{Software Engineer} \hfill \textit{Sep 2024 -- Dec 2024}
\begin{itemize}
    \item Delivered custom web applications, automation scripts, and product solutions for clients across multiple sectors, moving from early requirements to usable shipped software.
    \item Owned discovery, prioritization, development, launch, iteration, and technical support while working independently across frontend, backend, and data workflows.
\end{itemize}

\vspace{10pt}
\textbf{Asociacion Venezolano Americana de Amistad (AVAA)} \hfill \textit{Remote, Venezuela} \\
\textbf{Software Developer} \hfill \textit{Aug 2023 -- Sep 2024}
\begin{itemize}
    \item Built SEP, a production internal platform that replaced spreadsheet-heavy operations with live scholar records, activity tracking, volunteer-hour logs, attendance workflows, and reporting across 3 national chapters.
    \item Engineered SEA for EducationUSA, a full-stack internal tool that centralized advisee records, outreach activities, service history, payments, and institutional alliances into one operating system for advisors.
\end{itemize}

\vspace{10pt}
\textbf{Asociacion Venezolano Americana de Amistad (AVAA)} \hfill \textit{Caracas, Venezuela} \\
\textbf{Software Developer Intern} \hfill \textit{Oct 2022 -- Aug 2023}
\begin{itemize}
    \item Built an interactive Power BI dashboard that improved analytics workflows by turning scattered alumni data into usable reporting views.
    \item Wrote Python scripts to extract, normalize, and prepare historical data, reducing manual cleanup and improving reporting reliability.
\end{itemize}

\vspace{8pt}
\begin{center}
    \textbf{Selected Product Projects}
\end{center}
\vspace{-4pt}

\textbf{Billingua Talent} \hfill \textit{2025}
\begin{itemize}
    \item Designed and shipped a professional networking and operations platform connecting bilingual Venezuelan talent with job opportunities and advisor support services.
    \item Combined candidate profiles, service workflows, and operational dashboards in one product used for real-world decision-making and follow-up.
\end{itemize}

\vspace{6pt}
\textbf{Brio} \hfill \textit{Independent Project}
\begin{itemize}
    \item Built a mobile-first control plane for an AI agent system focused on pairing, session control, relay routing, logs, and operational visibility.
    \item Explored product patterns for AI agents, workflow orchestration, and operator-facing tooling at the intersection of software and AI systems.
\end{itemize}

\vspace{8pt}
\begin{center}
    \textbf{Leadership and Community}
\end{center}
\vspace{-4pt}

\textbf{JA Venezuela Alumni} \hfill \textit{Remote} \\
\textbf{Vice President} \hfill \textit{Mar 2026 -- Present}
\begin{itemize}
    \item Support strategy, partnerships, planning, and operations for the alumni network, contributing to founder-minded and entrepreneurship-focused community work.
\end{itemize}

\vspace{6pt}
\textbf{Technovation Girls Venezuela} \hfill \textit{Caracas, Venezuela} \\
\textbf{Code Mentor} \hfill \textit{Jan 2026 -- May 2026}
\begin{itemize}
    \item Mentored students through research, prototyping, technical troubleshooting, and mobile app development.
\end{itemize}

\vspace{8pt}
\begin{center}
    \textbf{Education}
\end{center}
\vspace{-4pt}

\textbf{Instituto de Estudios Superiores de Administracion (IESA)} \hfill \textit{Caracas, Venezuela} \\
Master of Public Administration \hfill \textit{In Progress}

\vspace{8pt}
\begin{center}
    \textbf{Languages}
\end{center}
\vspace{-4pt}

Spanish (Native), English (C1)

\end{document}
