\documentclass[11pt]{article}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{cmap}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage[left=1.2cm,top=1.4cm,right=1.2cm,bottom=1.2cm]{geometry}
\setlength{\parindent}{0pt}
\setlist[itemize]{leftmargin=*, noitemsep, topsep=2pt, partopsep=0pt, parsep=2pt, label={\textbf{-}}}

\begin{document}
\begin{center}
    {\LARGE \textbf{Kevin Bravo}}\\
    Software Engineer | Full-Stack Web Applications, Python \& Frontend Systems \\
    \hrulefill
\end{center}
\begin{center}
    \href{mailto:0bravokevin@gmail.com}{0bravokevin@gmail.com}
    \textbullet\ 
    \href{http://www.kevinbravo.com}{www.kevinbravo.com}
\end{center}
\vspace{4pt}
\begin{center}
    \textbf{Profile}
\end{center}
\vspace{-4pt}
Software engineer with 4+ years of experience building production-ready web applications, internal platforms, and data systems across startup, government, and non-profit environments. My work combines backend architecture, full-stack product delivery, responsive interface implementation, API integrations, Python workflows, and high-ownership execution from concept to production. I am especially interested in reliable software, AI tooling, and systems that need to be correct, maintainable, and useful in practice.
\vspace{8pt}
\begin{center}
    \textbf{Experience}
\end{center}
\vspace{-4pt}
\textbf{Proyecto Educa} \hfill \textit{Remote, Venezuela} \\
\textbf{Chief Technology Officer} \hfill \textit{Dec 2025 -- Present}
\begin{itemize}
    \item Own product and technical direction for education-focused digital initiatives, translating ambiguous operating needs into architecture, delivery plans, and implementation priorities.
    \item Lead hands-on execution across platform design, development workflows, and system decisions, with direct responsibility for what ships and how it evolves.
\end{itemize}
\vspace{10pt}
\textbf{Free2Z} \hfill \textit{Remote, Venezuela} \\
\textbf{Principal Software Engineer} \hfill \textit{Apr 2025 -- Apr 2026}
\begin{itemize}
    \item Led the migration of a production platform from React to SvelteKit, improving maintainability, frontend structure, and production performance.
    \item Integrated a Python/Django API with the frontend, shipped live video features, built a custom CMS suite, and improved SSR behavior for a better user experience.
    \item Worked across product, frontend, backend integration, and content workflows to ship user-facing features end to end.
\end{itemize}
\vspace{10pt}
\textbf{U.S. Department of State (via AVAA)} \hfill \textit{Remote, Venezuela} \\
\textbf{Software Engineer | Full-Stack Developer} \hfill \textit{Nov 2024 -- Aug 2025}
\begin{itemize}
    \item Built Billingua Talent as the sole engineer, owning the full lifecycle from data architecture and product flows to production delivery.
    \item Designed and implemented candidate profiles, advisor dashboards, service-management workflows, and reporting views for day-to-day operational use.
    \item Built public-facing and internal-facing features with attention to usability, maintainability, and responsive behavior.
\end{itemize}
\vspace{10pt}
\textbf{Freelance} \hfill \textit{Remote} \\
\textbf{Software Engineer} \hfill \textit{Sep 2024 -- Dec 2024}
\begin{itemize}
    \item Delivered custom web platforms, automation scripts, and end-to-end software solutions for clients across multiple sectors.
    \item Moved quickly from requirements to usable interfaces and working systems, often defining the product structure before implementation started.
\end{itemize}
\vspace{10pt}
\textbf{Asociacion Venezolano Americana de Amistad (AVAA)} \hfill \textit{Remote, Venezuela} \\
\textbf{Software Developer} \hfill \textit{Aug 2023 -- Sep 2024}
\begin{itemize}
    \item Built PES, a web platform that became the source of truth for scholar records, activities, attendance, volunteer hours, and reports across 3 AVAA chapters.
    \item Engineered SEA for EducationUSA, centralizing student histories, services, outreach activities, and institutional alliances into one operational platform.
    \item Worked on product structure, data organization, backend workflows, interface design, and reporting views for real operational use.
\end{itemize}
\vspace{10pt}
\textbf{Asociacion Venezolano Americana de Amistad (AVAA)} \hfill \textit{Caracas, Venezuela} \\
\textbf{Software Developer Intern} \hfill \textit{Oct 2022 -- Aug 2023}
\begin{itemize}
    \item Built a fully interactive Power BI dashboard that turned scattered alumni records into a clearer analytics workflow.
    \item Wrote Python scripts to extract, normalize, and prepare historical data, improving the reliability of downstream reporting.
\end{itemize}
\vspace{8pt}
\begin{center}
    \textbf{Education}
\end{center}
\vspace{-4pt}
\textbf{Instituto de Estudios Superiores de Administracion (IESA)} \hfill \textit{Caracas, Venezuela} \\
Master of Public Administration \hfill \textit{In Progress}
\vspace{8pt}
\begin{center}
    \textbf{Leadership \& volunteering}
\end{center}
\vspace{-4pt}
\textbf{JA Venezuela Alumni} \hfill \textit{Caracas, Venezuela} \\
\textbf{Vice President} \hfill \textit{Mar 2026 -- Present}
\begin{itemize}
    \item Support planning, partnerships, and institutional growth for the national alumni network.
\end{itemize}
\vspace{10pt}
\textbf{Technovation Girls Venezuela} \hfill \textit{Caracas, Venezuela} \\
\textbf{Code Mentor} \hfill \textit{Jan 2026 -- Present}
\begin{itemize}
    \item Mentor students through research, prototyping, technical troubleshooting, and application development.
\end{itemize}
\vspace{8pt}
\begin{center}
    \textbf{Skills}
\end{center}
\vspace{-4pt}
\textbf{Technical:} JavaScript, TypeScript, Python, Django, SQL, PostgreSQL, React, SvelteKit, Next.js, HTML, CSS, responsive web design, API design and integrations, backend engineering, frontend implementation, data modeling, automation scripting, Power BI, Docker.
\\[4pt]
\textbf{Professional:} High-ownership execution, product ownership, independent work, system design, technical leadership, cross-functional collaboration, mentoring, process improvement.
\\[4pt]
\textbf{Interests:} AI safety, AI tooling, reliable software, formal methods, trustworthy systems, distributed systems, developer platforms, cybersecurity.
\\[4pt]
\textbf{Languages:} Spanish (Native), English (C1).
\end{document}
