\documentclass[11pt]{article}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{cmap}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage[left=1.02cm,top=1.15cm,right=1.02cm,bottom=0.7cm]{geometry}
\setlength{\parindent}{0pt}
\setlist[itemize]{leftmargin=*, noitemsep, topsep=1pt, partopsep=0pt, parsep=1pt, label={\textbf{-}}}

\begin{document}

\begin{center}
    {\LARGE \textbf{Kevin Bravo}}\\
    Senior Software Engineer | Platform, AI Tooling, Full-Stack Systems \\
    \hrulefill
\end{center}

\begin{center}
    \href{mailto:0bravokevin@gmail.com}{0bravokevin@gmail.com}
    \textbullet\
    \href{https://kevinbravo.com}{kevinbravo.com}
    \textbullet\
    \href{https://github.com/0bkevin}{github.com/0bkevin}
    \textbullet\
    Remote, Venezuela
\end{center}

\vspace{4pt}
\begin{center}
    \textbf{Professional Summary}
\end{center}
\vspace{-4pt}
Senior software engineer with 5 years of experience building production web platforms, internal systems, developer-adjacent tooling, and AI-assisted workflows across startup, government, and nonprofit environments. Strong background in TypeScript, JavaScript, React, full-stack architecture, platform migrations, backend integrations, and turning ambiguous problems into shipped systems. I work best close to product and architecture, writing code regularly, owning technical direction, and improving the systems other people rely on. Daily user of AI coding tools including Cursor, Codex, Claude, and Gemini.

\vspace{6pt}
\begin{center}
    \textbf{Core Skills}
\end{center}
\vspace{-4pt}
\textbf{Languages and Frontend:} TypeScript, JavaScript, React, Next.js, Svelte, SvelteKit, HTML, CSS, Tailwind CSS, responsive UI, server-side rendering \\
\textbf{Backend and Systems:} Python, Django, SQL, PostgreSQL, REST APIs, backend architecture, service integrations, data modeling \\
\textbf{Platform and Tooling:} CMS tooling, workflow automation, internal platforms, offline-oriented product design, Tauri, SQLite, real-time features, AI-assisted development \\
\textbf{Infrastructure and Delivery:} Docker, Azure, deployment ownership, debugging, technical migrations, release quality

\vspace{6pt}
\begin{center}
    \textbf{Work Experience}
\end{center}
\vspace{-4pt}

\textbf{Proyecto Educa} \hfill \textit{Remote, Venezuela} \\
\textbf{Chief Technology Officer} \hfill \textit{Dec 2025 -- Present}
\begin{itemize}
    \item \textbf{Own product and technical direction} for education platforms, defining architecture, implementation priorities, and release standards across frontend, backend, testing, and delivery.
    \item \textbf{Translate rough operational needs into shipped systems} while coordinating stakeholders, shaping roadmaps, and staying hands-on in implementation.
\end{itemize}

\vspace{8pt}
\textbf{Free2Z} \hfill \textit{Remote, Venezuela} \\
\textbf{Principal Software Engineer} \hfill \textit{Apr 2025 -- Apr 2026}
\begin{itemize}
    \item \textbf{Led a production platform migration from React to SvelteKit}, improving maintainability, frontend architecture, server-side rendering, and performance for a live product.
    \item \textbf{Built core product and platform capabilities} by integrating Python and Django APIs, shipping live video features, and delivering a CMS suite for content and operational workflows.
\end{itemize}

\vspace{8pt}
\textbf{U.S. Department of State (via AVAA)} \hfill \textit{Remote, Venezuela} \\
\textbf{Software Engineer | Full-Stack Developer} \hfill \textit{Nov 2024 -- Aug 2025}
\begin{itemize}
    \item \textbf{Built Billingua Talent as the sole engineer}, owning requirements, relational data architecture, backend flows, dashboard design, and production delivery.
    \item \textbf{Shipped operational tooling and user-facing flows} including candidate profiles, advisor dashboards, reporting views, and service-management workflows used across multiple centers.
\end{itemize}

\vspace{8pt}
\textbf{Freelance} \hfill \textit{Remote} \\
\textbf{Software Engineer} \hfill \textit{Sep 2024 -- Dec 2024}
\begin{itemize}
    \item \textbf{Delivered custom full-stack products, automation scripts, and integrations} across multiple sectors, moving quickly from discovery to launch and iteration.
\end{itemize}

\vspace{8pt}
\textbf{Asociacion Venezolano Americana de Amistad (AVAA)} \hfill \textit{Remote, Venezuela} \\
\textbf{Software Developer} \hfill \textit{Oct 2022 -- Jul 2024}
\begin{itemize}
    \item \textbf{Built internal operating platforms} for scholar records, attendance, volunteer hours, services, payments, receipts, outreach, and reporting across multiple teams and chapters.
    \item \textbf{Replaced spreadsheet-heavy processes with live systems} that improved visibility, coordination, and day-to-day operational reliability.
\end{itemize}

\vspace{6pt}
\begin{center}
    \textbf{Selected Projects}
\end{center}
\vspace{-4pt}

\textbf{Brio} \hfill \textit{Independent Project}
\begin{itemize}
    \item \textbf{Built a mobile-first control plane for an AI agent system} focused on pairing, session control, relay routing, logs, and operational visibility.
    \item \textbf{Explored AI-native product patterns} around operator tooling, agent workflows, runtime visibility, and fast iteration loops.
\end{itemize}

\vspace{6pt}
\textbf{Orpan} \hfill \textit{Tauri, React, Tailwind CSS, SQLite}
\begin{itemize}
    \item \textbf{Contributed to a local-first desktop application} packaged with Tauri, combining a React interface, embedded SQLite, on-device text-to-speech, and deterministic offline study flows.
    \item \textbf{Worked close to runtime and product constraints} where responsiveness, packaging, local execution, and offline behavior all mattered.
\end{itemize}

\vspace{6pt}
\begin{center}
    \textbf{Leadership and Community}
\end{center}
\vspace{-4pt}

\textbf{JA Venezuela Alumni} \hfill \textit{Remote} \\
\textbf{Vice President} \hfill \textit{Mar 2026 -- Present}
\begin{itemize}
    \item \textbf{Support executive oversight and institutional growth} for the alumni network, partnering with the President on internal operations and strategic execution.
    \item \textbf{Lead initiatives across training, networking, representation, and alumni growth} with partners, sponsors, and the Junior Achievement national office.
\end{itemize}

\vspace{6pt}
\textbf{Asociacion Venezolano Americana de Amistad (AVAA)} \hfill \textit{Remote, Venezuela} \\
\textbf{Education Committee Member} \hfill \textit{Sep 2024 -- Present}
\begin{itemize}
    \item \textbf{Serve as a strategic volunteer and advisor for Programa Excelencia}, providing technical expertise and operational support to improve educational impact and organizational effectiveness.
    \item \textbf{Administer the Sistema de Evaluacion del Participante} and contribute to curriculum redesign, fundraising strategy, and long-term planning with senior leadership.
\end{itemize}

\vspace{6pt}
\textbf{Dev3pack} \hfill \textit{Caracas, Venezuela} \\
\textbf{Hackathon Hub Organizer} \hfill \textit{Apr 2026 -- May 2026}
\begin{itemize}
    \item Organized the Caracas hub for a global Web3 and AI hackathon, coordinating mentors, speakers, logistics, and participant support.
\end{itemize}

\vspace{6pt}
\begin{center}
    \textbf{Education}
\end{center}
\vspace{-4pt}
\textbf{Instituto de Estudios Superiores de Administracion (IESA)} \hfill \textit{Caracas, Venezuela} \\
Master of Public Administration \hfill \textit{In Progress}

\vspace{6pt}
\begin{center}
    \textbf{Languages}
\end{center}
\vspace{-4pt}
Spanish (Native), English (C1)

\end{document}
