\documentclass[10pt]{article}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{cmap}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage[left=1.03cm,top=1.02cm,right=1.03cm,bottom=0.62cm]{geometry}
\IfFileExists{glyphtounicode.tex}{\input{glyphtounicode}\pdfgentounicode=1}{}
\hypersetup{
    hidelinks,
    pdfauthor={Kevin Bravo},
    pdftitle={Kevin Bravo - Command Code Full Stack TypeScript Developer CV},
    pdfsubject={ATS-compliant CV for Full Stack TypeScript Developer role at Command Code},
    pdfkeywords={Full Stack TypeScript Developer, TypeScript, JavaScript, Node.js, React.js, Next.js, Hono, Cloudflare, AWS, serverless APIs, PostgreSQL, Supabase, SQLite, database schema design, AI coding agents, developer tools, developer experience, AI-assisted development}
}
\setlength{\parindent}{0pt}
\hyphenpenalty=10000
\exhyphenpenalty=10000
\emergencystretch=2em
\pagestyle{empty}
\setlist[itemize]{leftmargin=*, noitemsep, topsep=0pt, partopsep=0pt, parsep=0pt, label={\textbf{-}}}

\begin{document}
\raggedright

\begin{center}
    {\LARGE \textbf{Kevin Bravo}}\\
    Full Stack TypeScript Developer | AI Developer Tools, React \& Serverless APIs \\
    \hrulefill
\end{center}

\begin{center}
    Email: \href{mailto:0bravokevin@gmail.com}{0bravokevin@gmail.com}
    | Portfolio: \href{https://kevinbravo.com}{https://kevinbravo.com}
    | GitHub: \href{https://github.com/0bkevin}{https://github.com/0bkevin}
    | LinkedIn: \href{https://www.linkedin.com/in/0bkevin/}{https://www.linkedin.com/in/0bkevin}
    | Location: Remote, Venezuela, PST overlap available
\end{center}

\vspace{2pt}
\begin{center}
    \textbf{Professional Summary}
\end{center}
\vspace{-6pt}
Full stack software engineer with 5 years of experience building production web platforms, internal tools, dashboards, APIs, data workflows, and developer-adjacent AI systems. Strong background in TypeScript, JavaScript, React.js, Next.js, SvelteKit, Node.js web tooling, Python, Django, PostgreSQL, SQL, SQLite, database schema design, serverless API patterns, Cloudflare Pages/Workers, and end to end product ownership.

\vspace{4pt}
\begin{center}
    \textbf{Technical Skills}
\end{center}
\vspace{-6pt}
\textbf{Languages and frontend:} TypeScript, JavaScript, React.js, Next.js, SvelteKit, Astro, HTML, CSS, Tailwind CSS, SSR, responsive UI, performance, developer experience. \\
\textbf{Backend, cloud, and data:} Node.js web tooling, REST APIs, API routes, Hono-style routing, serverless APIs, Cloudflare Pages, Cloudflare Workers, Cloudflare Turnstile, AWS/Azure/GCP concepts, Docker, CI/CD concepts, PostgreSQL, SQL, SQLite, Supabase-compatible schema design, database design. \\
\textbf{AI and delivery:} AI coding agents, Codex, Claude, Cursor, Gemini, OpenCode, T3Code, LLM workflows, prompt iteration, code review, debugging, fast startup execution, independent ownership.

\vspace{4pt}
\begin{center}
    \textbf{Work Experience}
\end{center}
\vspace{-6pt}

\textbf{Proyecto Educa} \hfill \textit{Remote, Venezuela} \\
\textbf{Chief Technology Officer} \hfill \textit{Dec 2025 - Present}
\begin{itemize}
    \item \textbf{Own product and technical direction} for education platforms, translating ambiguous stakeholder needs into architecture, frontend and backend execution, automation, feature verification, release quality, and shipped software.
\end{itemize}

\vspace{3pt}
\textbf{Free2Z} \hfill \textit{Remote, Venezuela} \\
\textbf{Principal Software Engineer} \hfill \textit{Apr 2025 - Apr 2026}
\begin{itemize}
    \item \textbf{Led a production migration from React to SvelteKit}, improving architecture, SSR, maintainability, performance, state handling, and delivery speed for a live startup product.
    \item \textbf{Shipped full stack product features end to end} by connecting frontend flows to Python and Django APIs, integrating Dyte live video, and building a CMS suite with a Markdown editor and blog engine.
\end{itemize}

\vspace{3pt}
\textbf{U.S. Department of State (via AVAA)} \hfill \textit{Remote, Venezuela} \\
\textbf{Software Engineer | Full-Stack Developer} \hfill \textit{Nov 2024 - Aug 2025}
\begin{itemize}
    \item \textbf{Built Billingua Talent as the sole engineer}, owning requirements, relational data architecture, backend-connected product flows, dashboards, reporting, quality checks, and production delivery.
    \item \textbf{Designed candidate profiles, advisor dashboards, service management workflows, registration flows, analytics views, and access patterns} for a production platform used by multiple centers.
\end{itemize}

\vspace{3pt}
\textbf{Asociacion Venezolano Americana de Amistad (AVAA)} \hfill \textit{Remote, Venezuela} \\
\textbf{Software Developer} \hfill \textit{Oct 2022 - Jul 2024}
\begin{itemize}
    \item \textbf{Built SEP}, a production internal platform replacing spreadsheet operations with live scholar records, activity tracking, volunteer-hour logs, attendance workflows, reporting, and chapter visibility.
    \item \textbf{Engineered SEA for EducationUSA}, a full-stack advisory operations platform centralizing advisee records, outreach activities, service history, payments, receipts, and institutional alliances.
    \item \textbf{Built Power BI dashboards and Python data scripts} for analytics workflows, data cleanup, validation, and reporting reliability.
\end{itemize}

\vspace{4pt}
\begin{center}
    \textbf{Projects and Proof of Work}
\end{center}
\vspace{-6pt}

\textbf{AI-Assisted Engineering and Agent Tooling} \hfill \textit{Developer Tools}
\begin{itemize}
    \item \textbf{Use AI coding tools daily} including Codex, Claude, Cursor, Gemini, OpenCode, T3Code, and Pi for planning, debugging, implementation, refactoring, code review, model comparison, and research.
    \item \textbf{Maintain Hermes and build agent workflow tools} including Zrode and Brio for multi-provider coding workflows, session control, relay routing, logs, and operational visibility.
\end{itemize}

\vspace{3pt}
\textbf{Personal Portfolio Cloudflare Workflow} \hfill \textit{TypeScript, Astro, Cloudflare}
\begin{itemize}
    \item \textbf{Implemented a TypeScript API route with Cloudflare Turnstile verification}, Cloudflare Pages/Workers environment bindings, request validation, JSON responses, and email-service integration.
\end{itemize}

\vspace{4pt}
\begin{center}
    \textbf{Education and Leadership}
\end{center}
\vspace{-6pt}
\textbf{IESA:} Master of Public Administration, in progress. \textbf{Leadership:} Dev3pack Caracas hub organizer, JA Venezuela Alumni Vice President, Technovation Girls Venezuela code mentor. \textbf{Languages:} Spanish (Native), English (C1).

\end{document}
