\documentclass[10pt]{article}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{cmap}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage[left=1.05cm,top=0.92cm,right=1.05cm,bottom=0.78cm]{geometry}
\IfFileExists{glyphtounicode.tex}{\input{glyphtounicode}\pdfgentounicode=1}{}
\hypersetup{
    hidelinks,
    pdfauthor={Kevin Bravo},
    pdftitle={Kevin Bravo - Product Engineer Full-Stack Software Engineer CV},
    pdfsubject={Default CV for Product Engineer and Full-Stack Software Engineer roles focused on backend systems, infrastructure, internal platforms, and applied AI},
    pdfkeywords={Kevin Bravo, Product Engineer, Full-Stack Software Engineer, Backend Systems, Infrastructure, Internal Platforms, Applied AI, TypeScript, JavaScript, React, SvelteKit, Next.js, Python, Django, PostgreSQL, SQL, Azure, Cloudflare, Docker, AI agents, MCP, developer tools, internal tools, dashboards, data modeling}
}
\setlength{\parindent}{0pt}
\hyphenpenalty=10000
\exhyphenpenalty=10000
\emergencystretch=2em
\pagestyle{empty}
\setlist[itemize]{leftmargin=*, noitemsep, topsep=1pt, partopsep=0pt, parsep=1pt, label={\textbf{-}}}

\newcommand{\sectiontitle}[1]{%
    \vspace{5pt}
    \begin{center}
        \textbf{#1}
    \end{center}
    \vspace{-6pt}
}

\begin{document}
\raggedright

\begin{center}
    {\LARGE \textbf{Kevin Bravo}}\\
    Product Engineer / Full-Stack Software Engineer \\
    Backend Systems, Infrastructure, Internal Platforms \& Applied AI \\
    \hrulefill
\end{center}

\begin{center}
    Email: \href{mailto:0bravokevin@gmail.com}{0bravokevin@gmail.com}
    | Portfolio: \href{https://kevinbravo.com}{https://kevinbravo.com}
    | GitHub: \href{https://github.com/0bkevin}{https://github.com/0bkevin}
    | LinkedIn: \href{https://www.linkedin.com/in/0bkevin/}{https://www.linkedin.com/in/0bkevin}
    | Remote, Venezuela
\end{center}

\sectiontitle{Professional Summary}
Product-minded full-stack software engineer with 5 years of experience designing, building, deploying, maintaining, and supporting production systems across startup, government, nonprofit, freelance, and independent environments. Strong background in backend systems, internal platforms, dashboards, data modeling, API integrations, infrastructure-aware delivery, and applied AI workflows. I work best in high-ownership environments where ambiguous operational or technical problems need to become reliable software people actually use.

\sectiontitle{Technical Profile}
\textbf{Full-stack product engineering:} TypeScript, JavaScript, React, SvelteKit, Next.js, Astro, HTML, CSS, Tailwind CSS, responsive UI, server-side rendering, frontend architecture, user workflows, product iteration, and release ownership. \\
\textbf{Backend systems and data:} Python, Django, Node.js web tooling, REST APIs, PostgreSQL, SQL, SQLite, relational data modeling, schema design, reporting systems, dashboards, service integrations, ETL scripts, and workflow automation. \\
\textbf{Infrastructure and operations:} Azure deployments, Azure VPS operations, Cloudflare Pages/Workers, Cloudflare Turnstile, Docker, environment configuration, logs, production debugging, CI/CD concepts, AWS/Azure/GCP model API usage, and deployment ownership. \\
\textbf{Applied AI and developer tooling:} Codex, Claude, Cursor, Gemini, OpenCode, T3Code, Pi, LLM workflows, AI coding agents, MCP concepts, prompt iteration, model comparison, agent control planes, and AI-assisted implementation.

\sectiontitle{Work Experience}

\textbf{Proyecto Educa} \hfill \textit{Remote, Venezuela} \\
\textbf{Chief Technology Officer} \hfill \textit{Dec 2025 - Present}
\begin{itemize}
    \item \textbf{Own product and technical direction} for education platforms, translating stakeholder needs into architecture, implementation priorities, support workflows, testing expectations, and shipped software.
    \item \textbf{Lead hands-on execution across frontend, backend, automation, release quality, production issue handling, and system decisions} for products used in live operations.
\end{itemize}

\vspace{5pt}
\textbf{Free2Z} \hfill \textit{Remote, Venezuela} \\
\textbf{Principal Software Engineer} \hfill \textit{Apr 2025 - Apr 2026}
\begin{itemize}
    \item \textbf{Led a production migration from React to SvelteKit}, improving frontend architecture, SSR, maintainability, performance, state handling, and delivery speed for a live startup product.
    \item \textbf{Shipped full-stack product features end to end} by connecting frontend workflows to Python and Django APIs, integrating Dyte live video, and building a CMS suite with a Markdown editor and blog engine.
    \item \textbf{Worked across product, architecture, implementation, testing, and support}, improving user-facing behavior and internal publishing workflows in a fast-moving environment.
\end{itemize}

\vspace{5pt}
\textbf{U.S. Department of State (via AVAA)} \hfill \textit{Remote, Venezuela} \\
\textbf{Software Engineer | Full-Stack Developer} \hfill \textit{Nov 2024 - Aug 2025}
\begin{itemize}
    \item \textbf{Built Billingua Talent as the sole engineer}, owning requirements, relational data architecture, backend-connected product flows, dashboards, reporting, quality checks, deployment, and maintenance.
    \item \textbf{Designed candidate profiles, advisor dashboards, service-management workflows, registration flows, analytics views, and access patterns} for a production platform used across multiple centers.
    \item \textbf{Supported advisors and program operators} by turning feedback and recurring questions into clearer workflows, better reporting views, data fixes, and more reliable service-management flows.
\end{itemize}

\vspace{5pt}
\textbf{Freelance} \hfill \textit{Remote} \\
\textbf{Software Engineer} \hfill \textit{Sep 2024 - Dec 2024}
\begin{itemize}
    \item \textbf{Delivered custom web applications, frontend projects, automation scripts, and product solutions} across multiple sectors, owning discovery, development, launch, iteration, and support.
    \item \textbf{Built public frontend projects and professional websites} including Jenn Dolinski, Proyecto Educa, and Rodolfo Medina del Rio, with attention to responsive UI, content structure, forms, performance, and deployment.
\end{itemize}

\newpage

\vspace{5pt}
\textbf{Asociacion Venezolano Americana de Amistad (AVAA)} \hfill \textit{Remote, Venezuela} \\
\textbf{Software Developer} \hfill \textit{Oct 2022 - Jul 2024}
\begin{itemize}
    \item \textbf{Built, deployed, and maintained SEP on Azure}, replacing spreadsheet-heavy operations with live scholar records, activity tracking, volunteer-hour logs, attendance workflows, reporting, and chapter-level visibility across 3 national chapters.
    \item \textbf{Engineered SEA for EducationUSA}, a full-stack advisory operations platform centralizing advisee records, outreach activities, service history, payments, receipts, institutional alliances, and reporting support.
    \item \textbf{Served as technical owner for internal users}, handling issue reports, user support, data cleanup, workflow changes, reporting reliability, and Python scripts for analytics and validation.
\end{itemize}

\vspace{5pt}
\textbf{Asociacion Venezolano Americana de Amistad (AVAA)} \hfill \textit{Caracas, Venezuela} \\
\textbf{Software Developer Intern} \hfill \textit{Sep 2021 - Aug 2022}
\begin{itemize}
    \item \textbf{Built an interactive Power BI dashboard and Python data scripts} that improved analytics workflows, historical-data cleanup, validation, and reporting reliability.
\end{itemize}

\sectiontitle{Selected Projects}
\textbf{Billingua Talent:} Full-stack professional networking and operations platform for bilingual Venezuelan talent, combining candidate profiles, advisor dashboards, English-readiness tracking, service registration, analytics, and reporting. \\
\textbf{SEP and SEA:} Internal platforms for AVAA and EducationUSA that centralized scholar records, attendance, volunteer hours, advisee histories, services, payments, receipts, institutional alliances, and reporting workflows. \\
\textbf{Zrode and Brio:} Applied AI and agent tooling work. Zrode is an agentic development environment for multi-provider coding workflows. Brio is a mobile-first control plane with session control, relay routing, logs, and operational visibility. \\
\textbf{Personal portfolio and Cloudflare workflow:} Portfolio with case studies, technical writing, and a TypeScript API route using Cloudflare Turnstile, Pages/Workers environment bindings, request validation, JSON responses, email integration, and error handling.

\sectiontitle{Proof of Work}
\textbf{Portfolio and case studies:} \href{https://kevinbravo.com/projects}{https://kevinbravo.com/projects}
| \textbf{AMA profile:} \href{https://kevinbravo.com/me/ama/}{https://kevinbravo.com/me/ama/}
| \textbf{Technical writing:} \href{https://kevinbravo.com/0b}{https://kevinbravo.com/0b}
| \textbf{GitHub:} \href{https://github.com/0bkevin}{https://github.com/0bkevin}

\sectiontitle{Leadership and Community}
\textbf{JA Venezuela Alumni:} Vice President supporting strategy, partnerships, operations, and institutional growth for a national alumni network focused on entrepreneurship and youth leadership. \\
\textbf{AVAA Education Committee:} Technical and operational volunteer supporting Programa Excelencia, maintaining internal systems, improving workflows, and helping the team make data-informed decisions. \\
\textbf{Dev3pack:} Organized the Caracas hub for a global Web3 and AI hackathon, coordinating logistics, sponsors, speakers, mentors, and participant support. \\
\textbf{Technovation Girls Venezuela:} Code mentor guiding students through research, prototyping, technical troubleshooting, and mobile app development with MIT App Inventor.

\sectiontitle{Education}
\textbf{Instituto de Estudios Superiores de Administracion (IESA)} \hfill \textit{Caracas, Venezuela} \\
Master of Public Administration \hfill \textit{In Progress}

\vspace{3pt}
\textbf{Universidad Central de Venezuela} \hfill \textit{Caracas, Venezuela} \\
Occupational Therapy, Cum Laude \hfill \textit{2023}

\sectiontitle{Additional Skills}
\textbf{Technical:} TypeScript, JavaScript, React, SvelteKit, Next.js, Astro, Python, Django, SQL, PostgreSQL, SQLite, REST APIs, Docker, Azure, Cloudflare, Tailwind CSS, Power BI, data modeling, internal tools, dashboards, CMS tooling, workflow automation, AI-assisted development, agent tooling, MCP concepts, infrastructure support. \\
\textbf{Professional:} Product judgment, technical ownership, system design, operating in ambiguity, stakeholder communication, user support, written documentation, mentoring, cross-functional collaboration, fast iteration, production support. \\
\textbf{Languages:} Spanish (Native), English (C1).

\end{document}
