\documentclass[11pt]{article}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{cmap}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage[left=1.08cm,top=1.12cm,right=1.08cm,bottom=0.72cm]{geometry}
\IfFileExists{glyphtounicode.tex}{\input{glyphtounicode}\pdfgentounicode=1}{}
\hypersetup{
    hidelinks,
    pdfauthor={Kevin Bravo},
    pdftitle={Kevin Bravo - DeFi AI Full Stack Developer CV},
    pdfsubject={ATS-compliant CV for Full Stack Developer with AI capabilities role in DeFi},
    pdfkeywords={Full Stack Developer, DeFi, AI, TypeScript, React, Node.js, Python, Django, APIs, Web3, blockchain, smart contracts, vaults, AMM, lending protocols, dashboards, Docker, CI/CD, AI-assisted development}
}
\setlength{\parindent}{0pt}
\hyphenpenalty=10000
\exhyphenpenalty=10000
\emergencystretch=2em
\pagestyle{empty}
\setlist[itemize]{leftmargin=*, noitemsep, topsep=1pt, partopsep=0pt, parsep=1pt, label={\textbf{-}}}

\begin{document}
\raggedright

\begin{center}
    {\LARGE \textbf{Kevin Bravo}}\\
    Full Stack Developer | DeFi, AI Workflows, React \& TypeScript \\
    \hrulefill
\end{center}

\begin{center}
    Email: \href{mailto:0bravokevin@gmail.com}{0bravokevin@gmail.com}
    | Portfolio: \href{https://kevinbravo.com}{https://kevinbravo.com}
    | GitHub: \href{https://github.com/0bkevin}{https://github.com/0bkevin}
    | LinkedIn: \href{https://www.linkedin.com/in/0bkevin/}{https://www.linkedin.com/in/0bkevin}
    | Location: Remote, Venezuela
\end{center}

\vspace{4pt}
\begin{center}
    \textbf{Professional Summary}
\end{center}
\vspace{-4pt}
Full stack software engineer with 5 years of experience designing, building, testing, and shipping production web platforms, dashboards, APIs, internal tools, and data workflows across startup, government, nonprofit, and independent environments. Strong background in TypeScript, JavaScript, React, SvelteKit, Next.js, Python, Django, SQL, PostgreSQL, API integrations, analytics dashboards, and end to end product ownership. Web3 and DeFi experience through Ethernaut, Damn Vulnerable DeFi, Brownie, flash loans, lending pools, EVM concepts, and smart contract security research. Daily user of AI tools for planning, debugging, implementation, refactoring, and research.

\vspace{7pt}
\begin{center}
    \textbf{Core Competencies}
\end{center}
\vspace{-4pt}
\textbf{Frontend and product UI:} TypeScript, JavaScript, React, SvelteKit, Next.js, Tailwind CSS, responsive dashboards, user-facing workflows, server-side rendering, performance, and product iteration. \\
\textbf{Backend and APIs:} Python, Django, SQL, PostgreSQL, REST APIs, data modeling, service integrations, reporting systems, backend connected product flows, automation scripts, and Node.js web tooling. \\
\textbf{DeFi and Web3:} DeFi concepts, vault strategy concepts, AMMs, lending pools, flash loans, smart contract interactions, EVM, Brownie, Solidity concepts, Web3.py, blockchain tooling, and security fundamentals. \\
\textbf{AI and analytics:} AI-assisted development, LLM workflows, agent tooling, Python data workflows, analytics dashboards, risk signal thinking, data validation, model-assisted research, and automation.

\vspace{7pt}
\begin{center}
    \textbf{Work Experience}
\end{center}
\vspace{-4pt}

\textbf{Proyecto Educa} \hfill \textit{Remote, Venezuela} \\
\textbf{Chief Technology Officer} \hfill \textit{Dec 2025 -- Present}
\begin{itemize}
    \item \textbf{Own product and technical direction} for education platforms, translating ambiguous stakeholder needs into architecture, implementation priorities, testing expectations, and shipped software.
    \item \textbf{Lead hands-on execution across frontend, backend, automation, feature verification, release quality, and system decisions} for products used in live operations.
\end{itemize}

\vspace{6pt}
\textbf{Free2Z} \hfill \textit{Remote, Venezuela} \\
\textbf{Principal Software Engineer} \hfill \textit{Apr 2025 -- Apr 2026}
\begin{itemize}
    \item \textbf{Led a production migration from React to SvelteKit}, improving maintainability, frontend architecture, server-side rendering, performance, and delivery speed for a live startup product.
    \item \textbf{Shipped full stack product features end to end} by integrating Python and Django APIs, delivering live video with Dyte, and building a custom CMS suite for content and operational workflows.
\end{itemize}

\vspace{6pt}
\textbf{U.S. Department of State (via AVAA)} \hfill \textit{Remote, Venezuela} \\
\textbf{Software Engineer | Full-Stack Developer} \hfill \textit{Nov 2024 -- Aug 2025}
\begin{itemize}
    \item \textbf{Built Billingua Talent as the sole engineer}, owning requirements, relational data architecture, backend connected product flows, dashboards, reporting, quality checks, and production delivery.
    \item \textbf{Designed candidate profiles, advisor dashboards, service management workflows, registration flows, and reporting views} that supported operational decisions across multiple centers.
\end{itemize}

\vspace{6pt}
\textbf{Freelance} \hfill \textit{Remote} \\
\textbf{Software Engineer} \hfill \textit{Sep 2024 -- Dec 2024}
\begin{itemize}
    \item \textbf{Delivered custom web applications, automation scripts, and product solutions} for clients across multiple sectors, owning discovery, prioritization, development, launch, iteration, and support.
\end{itemize}

\vspace{6pt}
\textbf{Asociacion Venezolano Americana de Amistad (AVAA)} \hfill \textit{Remote, Venezuela} \\
\textbf{Software Developer} \hfill \textit{Oct 2022 -- Jul 2024}
\begin{itemize}
    \item \textbf{Built SEP}, a production internal platform that replaced spreadsheet-heavy operations with live scholar records, activity tracking, volunteer-hour logs, attendance workflows, reporting, and chapter-level visibility.
    \item \textbf{Engineered SEA for EducationUSA}, a full-stack operations platform centralizing advisee records, outreach activities, service history, payments, receipts, and institutional alliances.
\end{itemize}

\vspace{6pt}
\textbf{Asociacion Venezolano Americana de Amistad (AVAA)} \hfill \textit{Caracas, Venezuela} \\
\textbf{Software Developer Intern} \hfill \textit{Sep 2021 -- Aug 2022}
\begin{itemize}
    \item \textbf{Built an interactive Power BI dashboard and Python data scripts} that improved analytics workflows, data cleanup, validation, and reporting reliability.
\end{itemize}

\vspace{7pt}
\begin{center}
    \textbf{Projects and Proof of Work}
\end{center}
\vspace{-4pt}

\textbf{Web3 and DeFi Technical Writing} \hfill \textit{Independent}
\begin{itemize}
    \item Published walkthroughs on Ethernaut, Damn Vulnerable DeFi, Brownie, wallet behavior, flash loans, lending pools, smart contract security, and blockchain development concepts.
\end{itemize}

\vspace{6pt}
\textbf{AI-Assisted Engineering Workflow} \hfill \textit{Ongoing}
\begin{itemize}
    \item Use Codex, Claude, Cursor, Gemini, OpenCode, T3Code, and related tools daily for planning, debugging, implementation, refactoring, code review, technical research, and model comparison.
\end{itemize}

\vspace{7pt}
\begin{center}
    \textbf{Leadership}
\end{center}
\vspace{-4pt}
\textbf{Dev3pack:} Organized the Caracas hub for a global Web3 and AI hackathon. \textbf{JA Venezuela Alumni:} Vice President supporting strategy, partnerships, and operations. \textbf{Technovation Girls Venezuela:} Code mentor for student mobile app development.

\vspace{7pt}
\begin{center}
    \textbf{Education}
\end{center}
\vspace{-4pt}
\textbf{Instituto de Estudios Superiores de Administracion (IESA)} \hfill \textit{Caracas, Venezuela} \\
Master of Public Administration \hfill \textit{In Progress}

\vspace{7pt}
\begin{center}
    \textbf{Skills}
\end{center}
\vspace{-4pt}
\textbf{Technical:} TypeScript, JavaScript, React, SvelteKit, Next.js, Node.js web tooling, Python, Django, SQL, PostgreSQL, REST APIs, Tailwind CSS, Docker, Power BI, HTML, CSS, data modeling, API integrations, dashboards, internal tools, CMS tooling, server-side rendering, workflow automation, AI-assisted development. \\
\textbf{Web3 and DeFi:} Solidity concepts, EVM, Brownie, Web3.py, smart contract security, flash loans, lending pools, AMM concepts, vault strategy concepts, wallet behavior, blockchain tooling, secure smart contract interaction patterns. \\
\textbf{AI, Data, Delivery:} LLM workflows, AI coding agents, Python data scripts, analytics dashboards, data validation, risk signal thinking, recommender-system concepts, manual QA, regression checks, CI/CD concepts, secure coding habits, release ownership. \\
\textbf{Languages:} Spanish (Native), English (C1).

\end{document}
