\documentclass[11pt]{article}
\usepackage{hyperref}
\usepackage{cmap}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage[left=1.45cm,top=1.35cm,right=1.45cm,bottom=1.25cm]{geometry}
\IfFileExists{glyphtounicode.tex}{\input{glyphtounicode}\pdfgentounicode=1}{}
\hypersetup{
    hidelinks,
    pdfauthor={Kevin Bravo},
    pdftitle={Kevin Bravo - DeFi AI Full Stack Cover Letter},
    pdfsubject={Cover letter for Full Stack Developer with AI capabilities role in DeFi},
    pdfkeywords={Kevin Bravo, DeFi, Full Stack Developer, AI, TypeScript, React, Node.js, Python, Web3, smart contracts, vaults, RFQ, options, structured products}
}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0.52em}
\pagestyle{empty}
\hyphenpenalty=10000
\exhyphenpenalty=10000
\emergencystretch=2em

\begin{document}
\raggedright

\begin{center}
    {\LARGE \textbf{Kevin Bravo}}\\
    Full Stack Developer | DeFi, AI Workflows, React \& TypeScript \\
    \href{mailto:0bravokevin@gmail.com}{0bravokevin@gmail.com} |
    \href{https://kevinbravo.com}{https://kevinbravo.com} \\
    \href{https://github.com/0bkevin}{https://github.com/0bkevin} |
    \href{https://www.linkedin.com/in/0bkevin/}{https://www.linkedin.com/in/0bkevin}
\end{center}

\vspace{0.45em}

July 2, 2026

Hiring Team,

I am Kevin, a software engineer with 5 years of experience building and shipping production systems across startup, government, nonprofit, and independent environments. I wanted to reach out because I am interested in the Full Stack Developer with AI capabilities role. The work combines several areas I care about: full-stack product engineering, DeFi infrastructure, AI-assisted workflows, secure system design, and user-facing tools for financial decisions.

Your focus on a decentralized, multi-chain structured-products protocol stood out to me. RFQ architecture, options products, vault mechanics, dashboards, and API reliability all require engineering that is careful with data, state, user experience, and failure modes. I enjoy this kind of work because the product only works when the interface, backend logic, integrations, testing, and operational details line up.

Most of my experience has been in small, high-ownership environments where I owned features from requirements to production. At Free2Z, I led a production migration from React to SvelteKit, improved frontend architecture, connected the product to Python and Django APIs, shipped live video features with Dyte, and built a custom CMS suite. For the U.S. Department of State's Venezuela Affairs Unit, I built Billingua Talent as the sole engineer, covering requirements, data models, dashboards, advisor workflows, quality checks, and delivery.

At AVAA, I built SEP, an internal Participant Evaluation System that centralized scholar records, activity tracking, attendance, volunteer hours, and reporting across three chapters. That project shaped how I approach product engineering. I like understanding the workflow behind the feature, modeling the data correctly, building the interface people need, and testing the paths that will break during real use.

I have also been building depth in Web3 and DeFi through technical writing, study, and hands-on exercises. I have worked through and written about Ethernaut, Damn Vulnerable DeFi, Brownie, wallet behavior, flash loans, lending pools, smart contract security, and blockchain development concepts. I am careful about protocol assumptions and security boundaries, and I would bring that mindset to smart contract interactions, vault-related interfaces, and chain integrations.

AI-assisted engineering is part of my daily workflow. I use Codex, Claude, Cursor, Gemini, OpenCode, and related tools for planning, debugging, implementation, refactoring, code review, and research. I am especially interested in applying AI to intelligent dashboards, risk signals, user strategy recommendations, and automation that helps users make better DeFi decisions while keeping the implementation understandable and testable.

You can learn more about me here: \href{https://kevinbravo.com/me/ama/}{https://kevinbravo.com/me/ama/}

I would be glad to explore how I could help build the protocol UI, APIs, analytics workflows, AI-powered features, and secure product systems behind your structured-products platform.

Best,

Kevin

\end{document}
