\documentclass[11pt]{article}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{cmap}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage[left=1.2cm,top=1.4cm,right=1.2cm,bottom=1.2cm]{geometry}
\setlength{\parindent}{0pt}
\setlist[itemize]{leftmargin=*, noitemsep, topsep=2pt, partopsep=0pt, parsep=2pt, label={\textbf{-}}}
\begin{document}
\begin{center}
    {\LARGE \textbf{Kevin Bravo}}\\
    Software Engineer | Backend Systems, AI Infrastructure \& Full-Stack Product \\
    \hrulefill
\end{center}
\begin{center}
    \href{mailto:0bravokevin@gmail.com}{0bravokevin@gmail.com}
    \textbullet\ 
    \href{http://www.kevinbravo.com}{www.kevinbravo.com}
\end{center}
\vspace{4pt}
\begin{center}
    \textbf{Profile}
\end{center}
\vspace{-4pt}
Software engineer with 4+ years of experience building production-ready platforms, internal systems, and full-stack products across startup, government, and nonprofit environments. Built and maintained systems for the U.S. Department of State's Venezuela Affairs Unit, Free2Z, and AVAA, with a focus on backend architecture, AI-enabled engineering workflows, service integrations, data modeling, infrastructure-minded system design, and high-ownership execution from concept to production. I am especially interested in hard backend problems, AI systems, and products operating close to real customer workflows.
\vspace{8pt}
\begin{center}
    \textbf{Experience}
\end{center}
\vspace{-4pt}
\textbf{Proyecto Educa} \hfill \textit{Remote, Venezuela} \\
\textbf{Chief Technology Officer} \hfill \textit{Dec 2025 -- Present}
\begin{itemize}
    \item Own product and technical direction for education-focused digital initiatives, translating ambiguous operating needs into architecture, delivery plans, and implementation priorities.
    \item Lead hands-on execution across platform design, development workflows, and system decisions, with direct responsibility for what ships and how it evolves.
\end{itemize}
\vspace{10pt}
\textbf{Free2Z} \hfill \textit{Remote, Venezuela} \\
\textbf{Principal Software Engineer} \hfill \textit{Apr 2025 -- Apr 2026}
\begin{itemize}
    \item Directed the migration of a production platform from React to SvelteKit, redesigning core architecture for better performance, maintainability, and more reliable state handling.
    \item Integrated a Python/Django API with the new frontend, shipped live video via Dyte, built a custom CMS suite, and improved SSR behavior to strengthen production performance.
\end{itemize}
\vspace{10pt}
\textbf{U.S. Department of State (via AVAA)} \hfill \textit{Remote, Venezuela} \\
\textbf{Software Engineer | Full-Stack Developer} \hfill \textit{Nov 2024 -- Aug 2025}
\begin{itemize}
    \item Built Billingua Talent as the sole engineer, owning the full lifecycle from data architecture and backend-connected product flows to production delivery for the U.S. Department of State's Venezuela Affairs Unit.
    \item Designed candidate profiles, advisor dashboards, service-management workflows, and reporting views that improved talent visibility, English-readiness planning, and operational decision-making.
\end{itemize}
\vspace{10pt}
\textbf{Freelance} \hfill \textit{Remote} \\
\textbf{Software Engineer} \hfill \textit{Sep 2024 -- Dec 2024}
\begin{itemize}
    \item Delivered custom web platforms, automation scripts, and end-to-end software solutions for clients across multiple sectors, moving quickly from requirements to usable products.
    \item Owned projects from discovery and prioritization through development, launch, iteration, and technical support, often defining the structure before implementation started.
\end{itemize}
\vspace{10pt}
\textbf{Asociacion Venezolano Americana de Amistad (AVAA)} \hfill \textit{Remote, Venezuela} \\
\textbf{Software Developer} \hfill \textit{Aug 2023 -- Sep 2024}
\begin{itemize}
    \item Built PES, the source of truth for scholar records, activities, volunteer hours, attendance, and reports across 3 AVAA chapters, replacing fragmented spreadsheet workflows with a live operational system.
    \item Engineered SEA/AES for EducationUSA, centralizing student histories, outreach activities, services, and institutional alliances into one backend-driven advisory operations platform.
\end{itemize}
\vspace{10pt}
\textbf{Asociacion Venezolano Americana de Amistad (AVAA)} \hfill \textit{Caracas, Venezuela} \\
\textbf{Software Developer Intern} \hfill \textit{Oct 2022 -- Aug 2023}
\begin{itemize}
    \item Built a fully interactive Power BI dashboard that turned scattered alumni records into a clearer analytics workflow for AVAA.
    \item Wrote Python scripts to extract, normalize, and prepare historical data, reducing repetitive cleanup and improving the reliability of downstream reporting.
\end{itemize}
\vspace{8pt}
\begin{center}
    \textbf{Selected AI Work}
\end{center}
\vspace{-4pt}
\begin{itemize}
    \item Building Zrode, an agentic development environment designed to make coding agents feel like a real workspace instead of scattered terminal sessions, with support for multi-provider agent workflows.
    \item Building Brio, a mobile-first control plane for Hermes Agent focused on pairing, session control, relay routing, logs, and operational management for agent systems.
\end{itemize}
\vspace{8pt}
\begin{center}
    \textbf{Education}
\end{center}
\vspace{-4pt}
\textbf{Instituto de Estudios Superiores de Administracion (IESA)} \hfill \textit{Caracas, Venezuela} \\
Master of Public Administration \hfill \textit{In Progress}
\vspace{8pt}
\begin{center}
    \textbf{Leadership \& Volunteering}
\end{center}
\vspace{-4pt}
\textbf{JA Venezuela Alumni} \hfill \textit{Caracas, Venezuela} \\
\textbf{Vice President} \hfill \textit{Mar 2026 -- Present}
\begin{itemize}
    \item Support strategic planning, partnerships, and institutional growth for the national alumni network.
    \item Coordinate initiatives focused on entrepreneurship, professional leadership, and alumni engagement.
\end{itemize}
\vspace{10pt}
\textbf{Asociacion Venezolano Americana de Amistad (AVAA)} \hfill \textit{Remote, Venezuela} \\
\textbf{Education Committee Member} \hfill \textit{Sep 2024 -- Present}
\begin{itemize}
    \item Serve as primary administrator for PES, supporting scholarship follow-up operations across 3 AVAA chapters.
    \item Contribute to curriculum redesign, fundraising strategy, and long-term planning for Programa Excelencia.
\end{itemize}
\vspace{10pt}
\textbf{Technovation Girls Venezuela} \hfill \textit{Caracas, Venezuela} \\
\textbf{Code Mentor} \hfill \textit{Jan 2026 -- May 2026}
\begin{itemize}
    \item Mentor 4 students in the design and development of a mobile application using MIT App Inventor.
    \item Guide the team through research, prototyping, technical troubleshooting, and pitch preparation.
\end{itemize}
\vspace{8pt}
\begin{center}
    \textbf{Skills}
\end{center}
\vspace{-4pt}
\textbf{Technical:} TypeScript, JavaScript, Python, Django, SQL, Docker, PostgreSQL, SvelteKit, React, Next.js, Tailwind CSS, Power BI, backend engineering, AI infrastructure and agent systems, API design and integrations, distributed-systems thinking, data modeling, automation scripting, developer tooling.
\\[4pt]
\textbf{Professional:} High-ownership execution, technical leadership, product ownership, system design, cross-functional collaboration, mentoring, process improvement, working effectively in ambiguity, shipping from zero to production. \\[4pt]
\textbf{Languages:} Spanish (Native), English (C1). \\[4pt]
\textbf{Interests:} AI systems, voice and agent infrastructure, distributed systems, developer platforms, workflow automation, cybersecurity.
\end{document}
