\documentclass[11pt]{article}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{cmap}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage[left=1.15cm,top=1.35cm,right=1.15cm,bottom=0.9cm]{geometry}
\IfFileExists{glyphtounicode.tex}{\input{glyphtounicode}\pdfgentounicode=1}{}
\hypersetup{
    hidelinks,
    pdfauthor={Kevin Bravo},
    pdftitle={Kevin Bravo - Tech Lead and Agent Architect CV},
    pdfsubject={Curriculum vitae focused on SaaS architecture, AI agent systems, and engineering leadership},
    pdfkeywords={Kevin Bravo, Tech Lead, Agent Architect, SaaS Architecture, AI Agents, LLMs, TypeScript, React, SvelteKit, Python, Django, PostgreSQL}
}
\setlength{\parindent}{0pt}
\pagestyle{empty}
\setlist[itemize]{leftmargin=*, noitemsep, topsep=2pt, partopsep=0pt, parsep=2pt, label={\textbf{-}}}

\begin{document}

\begin{center}
    {\LARGE \textbf{Kevin Bravo}}\\
    Tech Lead | Agent Architect \\
    \hrulefill
\end{center}

\begin{center}
    \href{mailto:0bravokevin@gmail.com}{0bravokevin@gmail.com}
    \textbullet\
    \href{https://kevinbravo.com}{kevinbravo.com}
    \textbullet\
    \href{https://github.com/0bkevin}{github.com/0bkevin}
    \textbullet\
    \href{https://www.linkedin.com/in/0bkevin/}{linkedin.com/in/0bkevin}
    \textbullet\
    Remote, Venezuela
\end{center}

\vspace{4pt}
\begin{center}
    \textbf{Professional Summary}
\end{center}
\vspace{-4pt}
Software engineer with 5 years of experience designing and operating SaaS products, internal platforms, and AI agent systems across startup, government, and nonprofit environments. Currently CTO at Proyecto Educa, responsible for architecture, technical priorities, and software delivery. Led a production platform migration at Free2Z and independently built multi-tenant systems with role-based access, relational data models, and operational dashboards. Seeking a Tech Lead or Agent Architect role focused on system architecture, engineering leadership, and production software.

\vspace{8pt}
\begin{center}
    \textbf{Core Skills}
\end{center}
\vspace{-4pt}
\textbf{Architecture and Platforms:} SaaS architecture, multi-tenant systems, role-based access, relational data modeling, REST APIs, service integrations, internal platforms, production migrations \\
\textbf{AI Agents and LLMs:} agent control planes, multi-provider agent workflows, session management, relay routing, runtime logs, system health, LLM-assisted development \\
\textbf{Engineering Leadership:} team leadership, technical planning, architecture decisions, implementation priorities, stakeholder coordination, release management, production support \\
\textbf{Technology:} TypeScript, Next.js, SvelteKit, Python, Go, Django, PostgreSQL, Docker, Azure / AWS

\vspace{8pt}
\begin{center}
    \textbf{Work Experience}
\end{center}
\vspace{-4pt}

\textbf{Proyecto Educa} \hfill \textit{Remote, Venezuela} \\
\textbf{Chief Technology Officer} \hfill \textit{Dec 2025 -- Present}
\begin{itemize}
    \item \textbf{Set the architecture and technical priorities} for education platforms, translating operating requirements into system designs, implementation plans, and releases.
    \item \textbf{Lead software delivery across contributors and stakeholders}, setting development priorities, reviewing technical decisions, and remaining responsible for release quality and production support.
\end{itemize}

\vspace{10pt}
\textbf{Free2Z} \hfill \textit{Remote, Venezuela} \\
\textbf{Principal Software Engineer} \hfill \textit{Apr 2025 -- Apr 2026}
\begin{itemize}
    \item \textbf{Led the architecture and implementation of a production migration from React to SvelteKit}, improving maintainability, server-side rendering, state management, and performance for a live platform.
    \item \textbf{Defined integration patterns for Python and Django APIs} and delivered live video capabilities and a CMS suite used in customer-facing and publishing workflows.
\end{itemize}

\vspace{10pt}
\textbf{U.S. Department of State (via AVAA)} \hfill \textit{Remote, Venezuela} \\
\textbf{Product Engineer | Billingua Talent} \hfill \textit{Nov 2024 -- Aug 2025}
\begin{itemize}
    \item \textbf{Designed and built Billingua Talent as the sole engineer}, a multi-tenant SaaS platform with role-based access for candidates, employers, advisors, and administrators.
    \item \textbf{Owned the system from requirements through production}, including the relational data model, frontend and backend, dashboards, reporting, deployment, and maintenance.
    \item \textbf{Tested the platform with 50 users and 5 companies}, then revised workflows and reporting based on pilot feedback before the broader rollout.
\end{itemize}

\newpage
\textbf{Freelance} \hfill \textit{Remote} \\
\textbf{Software Engineer} \hfill \textit{Sep 2024 -- Dec 2024}
\begin{itemize}
    \item \textbf{Delivered full-stack product builds and automation scripts} across multiple sectors, moving from discovery and prioritization to launch, iteration, and technical support.
\end{itemize}

\vspace{10pt}
\textbf{Asociacion Venezolano Americana de Amistad (AVAA)} \hfill \textit{Remote, Venezuela} \\
\textbf{Junior Product Engineer} \hfill \textit{Oct 2022 -- Jul 2024}
\begin{itemize}
    \item \textbf{Designed, deployed, and maintained SEP}, a multi-tenant platform serving approximately 300 scholars across 3 national chapters with Auth.js, PostgreSQL, Prisma, and Azure.
    \item \textbf{Built SEA for EducationUSA}, centralizing student histories, payments, services, outreach, institutional relationships, and reporting in one platform.
    \item \textbf{Supported both systems in production}, resolving defects, maintaining data quality, and revising workflows based on staff feedback.
\end{itemize}

\vspace{10pt}
\textbf{Asociacion Venezolano Americana de Amistad (AVAA)} \hfill \textit{Caracas, Venezuela} \\
\textbf{Software Developer Intern} \hfill \textit{Sep 2021 -- Aug 2022}
\begin{itemize}
    \item \textbf{Built an interactive Power BI dashboard} and wrote Python data pipelines that improved reporting reliability and reduced manual cleanup for AVAA analytics workflows.
\end{itemize}

\vspace{8pt}
\begin{center}
    \textbf{Selected AI Agent Work}
\end{center}
\vspace{-4pt}
\textbf{Zrode:} Built and use an agent development environment for multi-provider coding workflows, with a unified interface for working with different coding agents during software development. \\
\textbf{Brio:} Built a mobile control plane for an AI agent system with device pairing, session control, relay routing, runtime logs, and health checks.

\vspace{8pt}
\begin{center}
    \textbf{Community and Leadership}
\end{center}
\vspace{-4pt}

\textbf{Dev3pack} \hfill \textit{Caracas, Venezuela} \\
\textbf{Hackathon Hub Organizer} \hfill \textit{Apr 2026 -- May 2026}
\begin{itemize}
    \item \textbf{Organized the Caracas hub for the Dev3pack Global Hackathon} focused on Web3 and AI, coordinating venue, sponsors, mentors, speakers, and participant support.
\end{itemize}

\vspace{6pt}
\textbf{JA Venezuela Alumni} \hfill \textit{Remote} \\
\textbf{Vice President} \hfill \textit{Mar 2026 -- Present}
\begin{itemize}
    \item Lead planning and delivery for training, partnerships, and community initiatives with the President, alumni team, and external organizations.
\end{itemize}

\vspace{6pt}
\textbf{Technovation Girls Venezuela} \hfill \textit{Caracas, Venezuela} \\
\textbf{Code Mentor} \hfill \textit{2026}
\begin{itemize}
    \item Guided a student team through problem definition, prototyping, technical decisions, and mobile application development with MIT App Inventor.
\end{itemize}

\vspace{8pt}
\begin{center}
    \textbf{Education}
\end{center}
\vspace{-4pt}
\textbf{Instituto de Estudios Superiores de Administracion (IESA)} \hfill \textit{Caracas, Venezuela} \\
Master of Public Administration \hfill \textit{In Progress}

\vspace{8pt}
\begin{center}
    \textbf{Languages}
\end{center}
\vspace{-4pt}
Spanish (Native), English (C1)

\end{document}
