\documentclass[11pt]{article}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{cmap}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage[left=1.2cm,top=1.4cm,right=1.2cm,bottom=1.2cm]{geometry}
\setlength{\parindent}{0pt}
\setlist[itemize]{leftmargin=*, noitemsep, topsep=2pt, partopsep=0pt, parsep=2pt, label={\textbf{-}}}

\begin{document}
\begin{center}
    {\LARGE \textbf{Kevin Bravo}}\\
    Founding Engineer | AI Agents, Backend Infrastructure \& Full-Stack Product \\
    \hrulefill
\end{center}
\begin{center}
    \href{mailto:0bravokevin@gmail.com}{0bravokevin@gmail.com}
    \textbullet\
    \href{https://www.kevinbravo.com}{www.kevinbravo.com}
    \textbullet\
    \href{https://github.com/0bkevin}{github.com/0bkevin}
    \textbullet\
    \href{https://www.linkedin.com/in/0bkevin/}{linkedin.com/in/0bkevin}
\end{center}
\vspace{4pt}
\begin{center}
    \textbf{Profile}
\end{center}
\vspace{-4pt}
Software engineer with 5 years of experience building production platforms, internal systems, backend-connected workflows, and full-stack products across startup, government, and nonprofit environments. Built systems for the U.S. Department of State's Venezuela Affairs Unit, Free2Z, and AVAA, often owning the full path from ambiguous problem to architecture, data model, implementation, launch, and iteration. Strong fit for founding engineer roles that need AI-native development, backend architecture, service integrations, distributed-systems thinking, product judgment, and fast zero-to-one shipping.

\vspace{8pt}
\begin{center}
    \textbf{Role Fit}
\end{center}
\vspace{-4pt}
\textbf{AI agents \& LLMs:} Daily user of Codex, Claude, Cursor, Gemini, OpenCode, T3Code, and related AI coding tools for task tracking, research, and daily workflows. \\
\textbf{Backend infrastructure:} Python, Django, SQL, PostgreSQL, REST APIs, data modeling, backend workflows, service integrations, Docker, SSR, live video integrations, and distributed-systems concepts. \\
\textbf{Full-stack product:} TypeScript, JavaScript, React, SvelteKit, Next.js, Tailwind CSS, dashboards, internal tools, CMS tooling, and user-facing workflows. \\
\textbf{Founder-style execution:} Comfortable wearing multiple hats across product, architecture, frontend, backend, data, delivery, stakeholder management, and operations.

\vspace{8pt}
\begin{center}
    \textbf{Experience}
\end{center}
\vspace{-4pt}
\textbf{Proyecto Educa} \hfill \textit{Remote, Venezuela} \\
\textbf{Chief Technology Officer} \hfill \textit{Dec 2025 -- Present}
\begin{itemize}
    \item Own product and technical direction for education-focused digital initiatives, translating ambiguous operating needs into architecture, delivery plans, and implementation priorities.
    \item Lead hands-on execution across platform design, development workflows, backend-connected product decisions, and release priorities.
\end{itemize}
\vspace{8pt}
\textbf{Free2Z} \hfill \textit{Remote, Venezuela} \\
\textbf{Principal Software Engineer} \hfill \textit{Apr 2025 -- Apr 2026}
\begin{itemize}
    \item Directed the migration of a production platform from React to SvelteKit, redesigning core architecture for better performance, maintainability, server-side rendering, and state handling.
    \item Integrated Python/Django APIs with the new frontend, shipped live video through Dyte, built a custom CMS suite, and improved production web performance for a live startup product.
\end{itemize}
\vspace{8pt}
\textbf{U.S. Department of State (via AVAA)} \hfill \textit{Remote, Venezuela} \\
\textbf{Software Engineer | Full-Stack Developer} \hfill \textit{Nov 2024 -- Aug 2025}
\begin{itemize}
    \item Built Billingua Talent as the sole engineer, owning requirements, relational data architecture, backend flows, dashboards, reporting, and production delivery.
    \item Designed candidate profiles, advisor dashboards, service-management workflows, registration flows, and reporting views that improved talent visibility, English-readiness planning, and operational follow-up across centers.
\end{itemize}
\vspace{8pt}
\textbf{Freelance} \hfill \textit{Remote} \\
\textbf{Software Engineer} \hfill \textit{Sep 2024 -- Dec 2024}
\begin{itemize}
    \item Delivered web platforms and automation scripts end to end, from discovery to launch, iteration, and support.
\end{itemize}
\vspace{8pt}
\textbf{Asociacion Venezolano Americana de Amistad (AVAA)} \hfill \textit{Remote, Venezuela} \\
\textbf{Software Developer} \hfill \textit{Oct 2022 -- Jul 2024}
\begin{itemize}
    \item Built SEP, the source of truth for scholar records, activities, volunteer hours, attendance, and reports across 3 AVAA chapters, replacing fragmented spreadsheet workflows with a live operational system.
    \item Engineered SEA/AES for EducationUSA, centralizing student histories, outreach activities, paid services, payments, receipts, and institutional alliances into one backend-driven advisory operations platform.
\end{itemize}
\vspace{8pt}
\textbf{Asociacion Venezolano Americana de Amistad (AVAA)} \hfill \textit{Caracas, Venezuela} \\
\textbf{Software Developer Intern} \hfill \textit{Sep 2021 -- Aug 2022}
\begin{itemize}
    \item Built an interactive Power BI dashboard and Python data scripts that transformed scattered alumni records into a cleaner analytics and reporting workflow.
\end{itemize}

\vspace{8pt}
\begin{center}
    \textbf{Selected AI \& Agent Work}
\end{center}
\vspace{-4pt}
\textbf{AI-native engineering workflow} \hfill \textit{Ongoing}
\begin{itemize}
    \item Use LLM and coding-agent tools daily to accelerate research, prototyping, debugging, architecture exploration, code review, implementation, and model comparison.
    \item Built Brio, a mobile-first control plane for pairing, session control, relay routing, logs, and operational visibility.
\end{itemize}

\vspace{8pt}
\begin{center}
    \textbf{Education}
\end{center}
\vspace{-4pt}
\textbf{Instituto de Estudios Superiores de Administracion (IESA)} \hfill \textit{Caracas, Venezuela} \\
Master of Public Administration \hfill \textit{In Progress}

\vspace{8pt}
\begin{center}
    \textbf{Leadership \& Volunteering}
\end{center}
\vspace{-4pt}
\textbf{Dev3pack:} Organized the Caracas hub for a global Web3 and AI hackathon, coordinating logistics, partnerships, speakers, mentors, and participant support. \\
\textbf{JA Venezuela Alumni:} Vice President supporting strategic planning, partnerships, operations, and institutional growth for the national alumni network. \\
\textbf{Technovation Girls Venezuela:} Code mentor guiding students through research, prototyping, technical troubleshooting, and mobile application development.

\vspace{8pt}
\begin{center}
    \textbf{Skills}
\end{center}
\vspace{-4pt}
\textbf{Technical:} TypeScript, JavaScript, Python, Django, SQL, Docker, PostgreSQL, SvelteKit, React, Next.js, Tailwind CSS, Power BI, backend engineering, REST APIs, data modeling, service integrations, workflow automation, dashboards, CMS tooling, SSR, live video integrations, AI agent tooling, LLM-assisted development, distributed-systems thinking.
\\[4pt]
\textbf{Professional:} Zero-to-one execution, founder-style ownership, technical leadership, product judgment, system design, stakeholder communication, mentoring, operating in ambiguity, wearing multiple hats, shipping fast without losing maintainability. \\[4pt]
\textbf{Languages:} Spanish (Native), English (C1). \\[4pt]
\textbf{Interests:} AI agents, LLM infrastructure, developer tools, backend platforms, distributed systems, cloud infrastructure, cybersecurity, blockchain infrastructure, education technology.
\end{document}
