\documentclass[10pt]{article}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{cmap}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage[left=0.96cm,top=0.86cm,right=0.96cm,bottom=0.56cm]{geometry}
\IfFileExists{glyphtounicode.tex}{\input{glyphtounicode}\pdfgentounicode=1}{}
\hypersetup{
    hidelinks,
    pdfauthor={Kevin Bravo},
    pdftitle={Kevin Bravo - Full Stack Engineer TypeScript React Node.js CV},
    pdfsubject={ATS-compliant CV for Full Stack Engineer role using TypeScript, React, and Node.js},
    pdfkeywords={Full Stack Engineer, TypeScript, React, React.js, Node.js, JavaScript, Next.js, SvelteKit, server-side TypeScript, backend APIs, REST APIs, PostgreSQL, SQL, cloud platforms, AWS, Azure, GCP, CI/CD, testing, code reviews, performance optimization, real-time applications, data visualization, financial markets, fintech, distributed systems}
}
\setlength{\parindent}{0pt}
\hyphenpenalty=10000
\exhyphenpenalty=10000
\emergencystretch=2em
\pagestyle{empty}
\setlist[itemize]{leftmargin=*, noitemsep, topsep=0pt, partopsep=0pt, parsep=0pt, label={\textbf{-}}}

\begin{document}
\raggedright

\begin{center}
    {\LARGE \textbf{Kevin Bravo}}\\
    Full Stack Engineer | TypeScript, React \& Node.js \\
    \hrulefill
\end{center}

\begin{center}
    Email: \href{mailto:0bravokevin@gmail.com}{0bravokevin@gmail.com}
    | Portfolio: \href{https://kevinbravo.com}{https://kevinbravo.com}
    | GitHub: \href{https://github.com/0bkevin}{https://github.com/0bkevin}
    | LinkedIn: \href{https://www.linkedin.com/in/0bkevin/}{https://www.linkedin.com/in/0bkevin}
    | Location: Remote, Venezuela
\end{center}

\vspace{2pt}
\begin{center}
    \textbf{Professional Summary}
\end{center}
\vspace{-6pt}
Full stack software engineer with 5 years of experience building production web applications, internal platforms, dashboards, APIs, workflow systems, and backend-connected product features across startup, government, nonprofit, and freelance environments. Strong background in TypeScript, JavaScript, React, SvelteKit, Next.js, Node.js web tooling, server-side TypeScript patterns, Python, Django, PostgreSQL, SQL, REST APIs, data modeling, frontend performance, cloud deployment, testing, code review, and end to end feature ownership.

\vspace{4pt}
\begin{center}
    \textbf{Technical Skills}
\end{center}
\vspace{-6pt}
\textbf{Frontend:} TypeScript, JavaScript, React.js, Next.js, SvelteKit, Astro, HTML, CSS, Tailwind CSS, responsive UI, frontend architecture, state management, SSR, performance optimization, data visualization. \\
\textbf{Backend and data:} Node.js web tooling, server-side TypeScript, API routes, REST APIs, Python, Django, PostgreSQL, SQL, SQLite, relational data modeling, service integrations, reporting systems. \\
\textbf{Engineering practices:} Git, code reviews, maintainable code, manual QA, regression checks, feature verification, release ownership, stack debugging, CI/CD concepts, Docker, Azure, Cloudflare, AWS/GCP concepts, real-time applications, distributed-systems concepts.

\vspace{4pt}
\begin{center}
    \textbf{Work Experience}
\end{center}
\vspace{-6pt}

\textbf{Proyecto Educa} \hfill \textit{Remote, Venezuela} \\
\textbf{Chief Technology Officer} \hfill \textit{Dec 2025 - Present}
\begin{itemize}
    \item \textbf{Own product and technical direction} for education platforms, translating stakeholder needs into architecture, implementation priorities, testing expectations, release quality, frontend and backend execution, and shipped software.
\end{itemize}

\vspace{3pt}
\textbf{Free2Z} \hfill \textit{Remote, Venezuela} \\
\textbf{Principal Software Engineer} \hfill \textit{Apr 2025 - Apr 2026}
\begin{itemize}
    \item \textbf{Led a production migration from React to SvelteKit}, improving frontend architecture, server-side rendering, maintainability, performance, state handling, and delivery speed for a live startup product.
    \item \textbf{Built and shipped backend-connected product features} by integrating frontend workflows with Python and Django APIs, delivering Dyte live video features, and building a custom CMS suite with a Markdown editor and blog engine.
\end{itemize}

\vspace{3pt}
\textbf{U.S. Department of State (via AVAA)} \hfill \textit{Remote, Venezuela} \\
\textbf{Software Engineer | Full-Stack Developer} \hfill \textit{Nov 2024 - Aug 2025}
\begin{itemize}
    \item \textbf{Built Billingua Talent as the sole engineer}, owning requirements, relational data architecture, backend-connected product flows, dashboards, reporting, quality checks, deployment, and maintenance.
    \item \textbf{Designed candidate profiles, advisor dashboards, registration flows, service-management workflows, analytics views, and access patterns} for a production platform used across centers.
\end{itemize}

\vspace{3pt}
\textbf{Freelance} \hfill \textit{Remote} \\
\textbf{Software Engineer} \hfill \textit{Sep 2024 - Dec 2024}
\begin{itemize}
    \item \textbf{Delivered custom web applications, frontend projects, automation scripts, and product solutions} across multiple sectors, including public websites for Jenn Dolinski, Proyecto Educa, and Rodolfo Medina del Rio.
\end{itemize}

\vspace{3pt}
\textbf{Asociacion Venezolano Americana de Amistad (AVAA)} \hfill \textit{Remote, Venezuela} \\
\textbf{Software Developer} \hfill \textit{Oct 2022 - Jul 2024}
\begin{itemize}
    \item \textbf{Built, deployed, and maintained SEP on Azure}, replacing spreadsheet-heavy operations with live scholar records, activity tracking, volunteer-hour logs, attendance workflows, reporting, and chapter visibility.
    \item \textbf{Engineered SEA for EducationUSA}, a full-stack operations platform centralizing advisee records, outreach activities, service history, payments, receipts, institutional alliances, and reporting.
    \item \textbf{Built Power BI dashboards and Python data scripts} for analytics, data cleanup, validation, historical reporting, and operational visibility.
\end{itemize}

\vspace{4pt}
\begin{center}
    \textbf{Selected Fit}
\end{center}
\vspace{-6pt}
\textbf{Server-side TypeScript and cloud:} Built a TypeScript API route with Cloudflare Turnstile verification, Pages/Workers environment bindings, request validation, JSON responses, email integration, and error handling. \\
\textbf{AI, financial, and real-time exposure:} Daily AI-assisted engineering workflow with Codex, Claude, Cursor, Gemini, and OpenCode; agent tooling with Zrode and Brio; Dyte live-video feature work; Power BI dashboards; Web3 and DeFi technical writing. \\
\textbf{Education and leadership:} IESA Master of Public Administration, in progress. Dev3pack Caracas hub organizer, JA Venezuela Alumni Vice President, Technovation Girls Venezuela code mentor. \\
\textbf{Languages:} Spanish (Native), English (C1).

\end{document}
