\documentclass[11pt]{article}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{cmap}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage[left=1.2cm,top=1.4cm,right=1.2cm,bottom=1.2cm]{geometry}
\setlength{\parindent}{0pt}
\setlist[itemize]{leftmargin=*, noitemsep, topsep=2pt, partopsep=0pt, parsep=2pt, label={\textbf{-}}}

\begin{document}
\begin{center}
    {\LARGE \textbf{Kevin Bravo}}\\
    Software Engineer | Full-Stack Platforms, Python Backends \& AI Tooling \\
    \hrulefill
\end{center}
\begin{center}
    \href{mailto:0bravokevin@gmail.com}{0bravokevin@gmail.com}
    \textbullet\ 
    \href{http://www.kevinbravo.com}{www.kevinbravo.com}
\end{center}
\vspace{4pt}
\begin{center}
    \textbf{Profile}
\end{center}
\vspace{-4pt}
Software engineer with 5 years of experience building production-ready web platforms, internal systems, and data-heavy products across startup, government, and nonprofit environments. My work has focused on taking ambiguous 0-to-1 problems into production through backend architecture, full-stack delivery, data modeling, API integrations, and operational tooling. I work comfortably across frontend and backend, use AI coding tools heavily in daily development, and care about building reliable systems that become useful infrastructure for the teams behind them.
\vspace{8pt}
\begin{center}
    \textbf{Experience}
\end{center}
\vspace{-4pt}
\textbf{Proyecto Educa} \hfill \textit{Remote, Venezuela} \\
\textbf{Chief Technology Officer} \hfill \textit{Dec 2025 -- Present}
\begin{itemize}
    \item Own product and technical direction for education-focused digital initiatives, translating ambiguous operational needs into architecture, delivery plans, and implementation priorities.
    \item Lead hands-on execution across platform design, development workflows, and system decisions, with direct responsibility for what ships and how it evolves.
\end{itemize}
\vspace{10pt}
\textbf{Free2Z} \hfill \textit{Remote, Venezuela} \\
\textbf{Principal Software Engineer} \hfill \textit{Apr 2025 -- Apr 2026}
\begin{itemize}
    \item Led the migration of a production platform from React to SvelteKit, improving maintainability, frontend structure, and production performance.
    \item Integrated a Python/Django API with the frontend, shipped live video features, built a custom CMS suite, and improved SSR behavior for a better user experience.
    \item Worked across product, frontend, backend integration, and content workflows to ship user-facing and internal-facing features end to end.
\end{itemize}
\vspace{10pt}
\textbf{U.S. Department of State (via AVAA)} \hfill \textit{Remote, Venezuela} \\
\textbf{Software Engineer | Full-Stack Developer} \hfill \textit{Nov 2024 -- Aug 2025}
\begin{itemize}
    \item Built Billingua Talent as the sole engineer, owning the full lifecycle from data architecture and product flows to production delivery.
    \item Designed and implemented candidate profiles, advisor dashboards, service-management workflows, and reporting views for day-to-day operational use.
    \item Built a platform that combined profile data, organizational workflows, and internal reporting into one system used by stakeholders across a distributed network.
\end{itemize}
\vspace{10pt}
\textbf{Freelance} \hfill \textit{Remote} \\
\textbf{Software Engineer} \hfill \textit{Sep 2024 -- Dec 2024}
\begin{itemize}
    \item Delivered custom web platforms, automation scripts, and end-to-end software solutions for clients across multiple sectors.
    \item Moved quickly from rough requirements to usable systems, often defining product structure, implementation approach, and development priorities independently.
\end{itemize}
\vspace{10pt}
\textbf{Asociacion Venezolano Americana de Amistad (AVAA)} \hfill \textit{Remote, Venezuela} \\
\textbf{Software Developer} \hfill \textit{Oct 2022 -- Jul 2024}
\begin{itemize}
    \item Built PES, a web platform that became the source of truth for scholar records, activities, attendance, volunteer hours, and reports across 3 AVAA chapters.
    \item Engineered SEA for EducationUSA, centralizing student histories, services, outreach activities, and institutional alliances into one operational platform.
    \item Worked on product structure, data organization, backend workflows, interface design, and reporting views for real operational use.
\end{itemize}
\vspace{10pt}
\textbf{Asociacion Venezolano Americana de Amistad (AVAA)} \hfill \textit{Caracas, Venezuela} \\
\textbf{Software Developer Intern} \hfill \textit{Sep 2021 -- Aug 2022}
\begin{itemize}
    \item Built a fully interactive Power BI dashboard that turned scattered alumni records into a clearer analytics workflow.
    \item Wrote Python scripts to extract, normalize, and prepare historical data, improving the reliability of downstream reporting.
\end{itemize}
\vspace{8pt}
\begin{center}
    \textbf{AI workflow}
\end{center}
\vspace{-4pt}
\begin{itemize}
    \item Daily user of AI coding tools for research, prototyping, debugging, architecture exploration, and implementation. Current workflow includes Codex, Claude, Gemini, Cursor, OpenCode, and related tools.
    \item Maintain a personal AI agent on a VPS to support task tracking, research, and daily technical workflows.
\end{itemize}
\vspace{8pt}
\begin{center}
    \textbf{Education}
\end{center}
\vspace{-4pt}
\textbf{Instituto de Estudios Superiores de Administracion (IESA)} \hfill \textit{Caracas, Venezuela} \\
Master of Public Administration \hfill \textit{In Progress}
\vspace{8pt}
\begin{center}
    \textbf{Leadership \& volunteering}
\end{center}
\vspace{-4pt}
\textbf{JA Venezuela Alumni} \hfill \textit{Caracas, Venezuela} \\
\textbf{Vice President} \hfill \textit{Mar 2026 -- Present}
\begin{itemize}
    \item Support planning, partnerships, and institutional growth for the national alumni network.
\end{itemize}
\vspace{10pt}
\textbf{Asociacion Venezolano Americana de Amistad (AVAA)} \hfill \textit{Remote, Venezuela} \\
\textbf{Education Committee Member} \hfill \textit{Sep 2024 -- Present}
\begin{itemize}
    \item Serve as a strategic volunteer supporting scholarship operations, system administration, and long-term program planning.
\end{itemize}
\vspace{8pt}
\begin{center}
    \textbf{Skills}
\end{center}
\vspace{-4pt}
\textbf{Technical:} TypeScript, JavaScript, Python, Django, SQL, PostgreSQL, React, SvelteKit, Next.js, HTML, CSS, Tailwind CSS, backend engineering, frontend implementation, API design and integrations, data modeling, automation scripting, Docker, Power BI.
\\[4pt]
\textbf{Professional:} High-ownership execution, product ownership, independent work, system design, stakeholder collaboration, technical leadership, shipping from zero to production, working effectively in ambiguity.
\\[4pt]
\textbf{Interests:} AI tooling, agentic systems, reliable software, nonprofit infrastructure, distributed systems, developer platforms, trustworthy systems.
\\[4pt]
\textbf{Languages:} Spanish (Native), English (C1).
\end{document}
