\documentclass[11pt]{article}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{cmap}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage[left=1.08cm,top=1.2cm,right=1.08cm,bottom=0.75cm]{geometry}
\setlength{\parindent}{0pt}
\setlist[itemize]{leftmargin=*, noitemsep, topsep=1pt, partopsep=0pt, parsep=1pt, label={\textbf{-}}}

\begin{document}

\begin{center}
    {\LARGE \textbf{Kevin Bravo}}\\
    Software Engineer | Automation, Internal Tools, Full-Stack Systems \\
    \hrulefill
\end{center}

\begin{center}
    \href{mailto:0bravokevin@gmail.com}{0bravokevin@gmail.com}
    \textbullet\
    \href{https://kevinbravo.com}{kevinbravo.com}
    \textbullet\
    \href{https://github.com/0bkevin}{github.com/0bkevin}
    \textbullet\
    Remote, Venezuela
\end{center}

\vspace{4pt}
\begin{center}
    \textbf{Professional Summary}
\end{center}
\vspace{-4pt}
Software engineer with 4+ years of experience building internal platforms, automation-heavy workflows, dashboards, and production web systems across startup, government, and nonprofit environments. Strong background in Python, TypeScript, full-stack delivery, data modeling, operational tooling, and turning ambiguous problems into maintainable systems that teams can rely on. I work well in small remote teams, move comfortably across product and infrastructure concerns, and am especially interested in AI tooling, reliable software, and research-adjacent systems.

\vspace{6pt}
\begin{center}
    \textbf{Core Skills}
\end{center}
\vspace{-4pt}
\textbf{Languages and Frameworks:} Python, TypeScript, JavaScript, React, SvelteKit, Next.js, Django, HTML, CSS \\
\textbf{Systems and Data:} SQL, PostgreSQL, REST APIs, ETL, data modeling, backend workflows, dashboards, reporting systems \\
\textbf{Delivery:} internal tools, workflow automation, full-stack product delivery, debugging, release ownership, remote collaboration \\
\textbf{Interests:} AI tooling, trustworthy systems, research infrastructure, AI safety and alignment

\vspace{6pt}
\begin{center}
    \textbf{Work Experience}
\end{center}
\vspace{-4pt}

\textbf{Proyecto Educa} \hfill \textit{Remote, Venezuela} \\
\textbf{Chief Technology Officer} \hfill \textit{Dec 2025 -- Present}
\begin{itemize}
    \item \textbf{Own product and technical direction} for education platforms, translating ambiguous operational needs into implementation plans, system design, and shipped software.
    \item \textbf{Lead hands-on execution across frontend, backend, testing, and workflow automation} for systems used in live organizational operations.
\end{itemize}

\vspace{8pt}
\textbf{Free2Z} \hfill \textit{Remote, Venezuela} \\
\textbf{Principal Software Engineer} \hfill \textit{Apr 2025 -- Apr 2026}
\begin{itemize}
    \item \textbf{Led a production migration from React to SvelteKit}, improving maintainability, performance, server-side rendering, and delivery speed for a live product.
    \item \textbf{Integrated Python and Django APIs, shipped live features, and built CMS and operations tooling} that reduced manual publishing work and improved internal workflows.
\end{itemize}

\vspace{8pt}
\textbf{U.S. Department of State (via AVAA)} \hfill \textit{Remote, Venezuela} \\
\textbf{Software Engineer | Full-Stack Developer} \hfill \textit{Nov 2024 -- Aug 2025}
\begin{itemize}
    \item \textbf{Built Billingua Talent as the sole engineer}, owning the full lifecycle from relational data architecture and backend flows to dashboards, reporting, and production delivery.
    \item \textbf{Shipped internal and user-facing tooling} for candidate profiles, advisor workflows, registrations, and reporting used for real-time operational follow-up.
\end{itemize}

\vspace{8pt}
\textbf{Freelance} \hfill \textit{Remote} \\
\textbf{Software Engineer} \hfill \textit{Sep 2024 -- Dec 2024}
\begin{itemize}
    \item \textbf{Delivered custom web platforms, automation scripts, and internal tools} across multiple sectors, moving from ambiguous requirements to shipped software quickly.
\end{itemize}

\vspace{8pt}
\textbf{Asociacion Venezolano Americana de Amistad (AVAA)} \hfill \textit{Remote, Venezuela} \\
\textbf{Software Developer} \hfill \textit{Aug 2023 -- Sep 2024}
\begin{itemize}
    \item \textbf{Built operational platforms that replaced spreadsheet-heavy workflows} for scholar records, attendance, volunteer hours, paid services, receipts, outreach, and reporting across multiple teams.
    \item \textbf{Engineered SEA and SEP as systems of record} that improved visibility, coordination, and day-to-day operational reliability across chapters and advisors.
\end{itemize}

\vspace{8pt}
\textbf{Asociacion Venezolano Americana de Amistad (AVAA)} \hfill \textit{Caracas, Venezuela} \\
\textbf{Software Developer Intern} \hfill \textit{Oct 2022 -- Aug 2023}
\begin{itemize}
    \item \textbf{Built an interactive Power BI dashboard and Python data scripts} that improved analytics workflows, ETL reliability, and reporting quality.
\end{itemize}

\vspace{6pt}
\begin{center}
    \textbf{Selected Projects}
\end{center}
\vspace{-4pt}

\textbf{Brio} \hfill \textit{Independent Project}
\begin{itemize}
    \item \textbf{Built a mobile-first control plane for an AI agent system} focused on pairing, session control, relay routing, logs, and operational visibility.
    \item \textbf{Used AI coding tools daily} including Codex, Cursor, Claude, and Gemini to research, prototype, and ship faster.
\end{itemize}

\vspace{6pt}
\begin{center}
    \textbf{Leadership and Community}
\end{center}
\vspace{-4pt}

\textbf{Asociacion Venezolano Americana de Amistad (AVAA)} \hfill \textit{Remote, Venezuela} \\
\textbf{Education Committee Member} \hfill \textit{Sep 2024 -- Present}
\begin{itemize}
    \item \textbf{Serve as a strategic volunteer and technical advisor for Programa Excelencia}, administering core systems and contributing to curriculum redesign, fundraising strategy, and long-term planning.
\end{itemize}

\vspace{6pt}
\textbf{JA Venezuela Alumni} \hfill \textit{Remote} \\
\textbf{Vice President} \hfill \textit{Mar 2026 -- Present}
\begin{itemize}
    \item \textbf{Support strategy, operations, and institutional growth} for a distributed alumni network, coordinating initiatives, partnerships, and community programs.
\end{itemize}

\vspace{6pt}
\textbf{Dev3pack} \hfill \textit{Caracas, Venezuela} \\
\textbf{Hackathon Hub Organizer} \hfill \textit{Apr 2026 -- May 2026}
\begin{itemize}
    \item \textbf{Organized the Caracas hub for a global Web3 and AI hackathon}, coordinating logistics, speakers, mentors, and participant support.
\end{itemize}

\vspace{6pt}
\begin{center}
    \textbf{Education}
\end{center}
\vspace{-4pt}
\textbf{Instituto de Estudios Superiores de Administracion (IESA)} \hfill \textit{Caracas, Venezuela} \\
Master of Public Administration \hfill \textit{In Progress}

\vspace{6pt}
\begin{center}
    \textbf{Languages}
\end{center}
\vspace{-4pt}
Spanish (Native), English (C1)

\end{document}
