\documentclass[11pt]{article}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{cmap}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage[left=1.2cm,top=1.4cm,right=1.2cm,bottom=1.2cm]{geometry}
\setlength{\parindent}{0pt}
\setlist[itemize]{leftmargin=*, noitemsep, topsep=2pt, partopsep=0pt, parsep=2pt, label={\textbf{-}}}

\begin{document}
\begin{center}
    {\LARGE \textbf{Kevin Bravo}}\\
    Software Engineer | Full-Stack Systems, Data Workflows \& AI Coding Tools \\
    \hrulefill
\end{center}
\begin{center}
    \href{mailto:0bravokevin@gmail.com}{0bravokevin@gmail.com}
    \textbullet\ 
    \href{http://www.kevinbravo.com}{www.kevinbravo.com}
\end{center}
\vspace{4pt}
\begin{center}
    \textbf{Profile}
\end{center}
\vspace{-4pt}
Software engineer with 4+ years of experience building production-ready web applications, internal platforms, and data systems across startup, government, and nonprofit environments. My work has focused on turning ambiguous operational needs into reliable software through backend architecture, full-stack delivery, data modeling, admin tooling, analytics workflows, and high-ownership execution from concept to production. I work well independently, use AI coding tools heavily in daily development, and care about building systems that handle sensitive data carefully and remain practical for the people who rely on them.
\vspace{8pt}
\begin{center}
    \textbf{Experience}
\end{center}
\vspace{-4pt}
\textbf{Proyecto Educa} \hfill \textit{Remote, Venezuela} \\
\textbf{Chief Technology Officer} \hfill \textit{Dec 2025 -- Present}
\begin{itemize}
    \item Own product and technical direction for education-focused digital initiatives, translating ambiguous operational needs into architecture, delivery plans, and implementation priorities.
    \item Lead hands-on execution across platform design, development workflows, and system decisions, with direct responsibility for what ships and how it evolves.
\end{itemize}
\vspace{10pt}
\textbf{Free2Z} \hfill \textit{Remote, Venezuela} \\
\textbf{Principal Software Engineer} \hfill \textit{Apr 2025 -- Apr 2026}
\begin{itemize}
    \item Led the migration of a production platform from React to SvelteKit, improving maintainability, frontend structure, and production performance.
    \item Integrated a Python/Django API with the frontend, shipped live video features, built a custom CMS suite, and improved SSR behavior for a better user experience.
    \item Worked across product, frontend, backend integration, and content workflows to ship user-facing and internal-facing features end to end.
\end{itemize}
\vspace{10pt}
\textbf{U.S. Department of State (via AVAA)} \hfill \textit{Remote, Venezuela} \\
\textbf{Software Engineer | Full-Stack Developer} \hfill \textit{Nov 2024 -- Aug 2025}
\begin{itemize}
    \item Built Billingua Talent as the sole engineer, owning the full lifecycle from data architecture and product flows to production delivery.
    \item Designed and implemented candidate profiles, advisor dashboards, service-management workflows, and reporting views for day-to-day operational use.
    \item Built public-facing and internal-facing features around profile data, service participation, and organizational reporting, with strong attention to usability and maintainability.
\end{itemize}
\vspace{10pt}
\textbf{Freelance} \hfill \textit{Remote} \\
\textbf{Software Engineer} \hfill \textit{Sep 2024 -- Dec 2024}
\begin{itemize}
    \item Delivered custom web platforms, automation scripts, and end-to-end software solutions for clients across multiple sectors.
    \item Moved quickly from rough requirements to usable systems, often defining product structure, implementation approach, and development priorities independently.
\end{itemize}
\vspace{10pt}
\textbf{Asociacion Venezolano Americana de Amistad (AVAA)} \hfill \textit{Remote, Venezuela} \\
\textbf{Software Developer} \hfill \textit{Aug 2023 -- Sep 2024}
\begin{itemize}
    \item Built PES, a web platform that became the source of truth for scholar records, activities, attendance, volunteer hours, and reports across 3 AVAA chapters.
    \item Engineered SEA for EducationUSA, centralizing student histories, services, outreach activities, and institutional alliances into one operational platform.
    \item Worked on product structure, data organization, backend workflows, interface design, participant-facing views, and reporting tools for real operational use.
\end{itemize}
\vspace{10pt}
\textbf{Asociacion Venezolano Americana de Amistad (AVAA)} \hfill \textit{Caracas, Venezuela} \\
\textbf{Software Developer Intern} \hfill \textit{Oct 2022 -- Aug 2023}
\begin{itemize}
    \item Built a fully interactive Power BI dashboard that turned scattered alumni records into a clearer analytics workflow.
    \item Wrote Python scripts to extract, normalize, and prepare historical data, improving the reliability of downstream reporting.
\end{itemize}
\vspace{8pt}
\begin{center}
    \textbf{Relevant strengths}
\end{center}
\vspace{-4pt}
\begin{itemize}
    \item Experience building systems that organize sensitive personal and operational data, including candidate records, scholar records, service participation, and internal reporting workflows.
    \item Strong fit for high-agency contract work. Much of my background has involved defining scope, designing data models, shipping internal tools, and handling ambiguous product decisions without heavy supervision.
    \item Daily user of AI coding tools for research, prototyping, debugging, and implementation. I use them to accelerate delivery while keeping engineering judgment and system quality in the loop.
\end{itemize}
\vspace{8pt}
\begin{center}
    \textbf{Education}
\end{center}
\vspace{-4pt}
\textbf{Instituto de Estudios Superiores de Administracion (IESA)} \hfill \textit{Caracas, Venezuela} \\
Master of Public Administration \hfill \textit{In Progress}
\vspace{8pt}
\begin{center}
    \textbf{Leadership \& volunteering}
\end{center}
\vspace{-4pt}
\textbf{JA Venezuela Alumni} \hfill \textit{Caracas, Venezuela} \\
\textbf{Vice President} \hfill \textit{Mar 2026 -- Present}
\begin{itemize}
    \item Support planning, partnerships, and institutional growth for the national alumni network.
\end{itemize}
\vspace{10pt}
\textbf{Technovation Girls Venezuela} \hfill \textit{Caracas, Venezuela} \\
\textbf{Code Mentor} \hfill \textit{Jan 2026 -- Present}
\begin{itemize}
    \item Mentor students through research, prototyping, technical troubleshooting, and application development.
\end{itemize}
\vspace{8pt}
\begin{center}
    \textbf{Skills}
\end{center}
\vspace{-4pt}
\textbf{Technical:} TypeScript, JavaScript, Python, Django, SQL, PostgreSQL, React, SvelteKit, Next.js, HTML, CSS, responsive web design, backend engineering, API design and integrations, data modeling, admin tooling, dashboard development, automation scripting, Docker, Power BI.
\\[4pt]
\textbf{Professional:} High-ownership execution, independent work, product ownership, system design, stakeholder collaboration, technical leadership, process improvement, shipping from zero to production.
\\[4pt]
\textbf{Interests:} AI safety, AI tooling, reliable software, talent infrastructure, trustworthy systems, nonprofit technology, distributed systems, developer platforms.
\\[4pt]
\textbf{Languages:} Spanish (Native), English (C1).
\end{document}
