\documentclass[11pt]{article}
\usepackage{hyperref}
\usepackage{cmap}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage[left=1.45cm,top=1.35cm,right=1.45cm,bottom=1.25cm]{geometry}
\IfFileExists{glyphtounicode.tex}{\input{glyphtounicode}\pdfgentounicode=1}{}
\hypersetup{
    hidelinks,
    pdfauthor={Kevin Bravo},
    pdftitle={Kevin Bravo - Limitless Cover Letter},
    pdfsubject={Cover letter for Senior Full-Stack Engineer role at Limitless},
    pdfkeywords={Kevin Bravo, Limitless, Senior Full-Stack Engineer, Product Engineer, TypeScript, Node.js, React, SvelteKit, AI-assisted development, Web3, DeFi}
}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0.55em}
\pagestyle{empty}
\hyphenpenalty=10000
\exhyphenpenalty=10000
\emergencystretch=2em

\begin{document}
\raggedright

\begin{center}
    {\LARGE \textbf{Kevin Bravo}}\\
    Senior Full-Stack Engineer | Product Builder, TypeScript \& AI Workflows \\
    \href{mailto:0bravokevin@gmail.com}{0bravokevin@gmail.com} |
    \href{https://kevinbravo.com}{https://kevinbravo.com} \\
    \href{https://github.com/0bkevin}{https://github.com/0bkevin} |
    \href{https://www.linkedin.com/in/0bkevin/}{https://www.linkedin.com/in/0bkevin}
\end{center}

\vspace{0.5em}

July 1, 2026

Limitless Hiring Team,

I am Kevin, a software engineer with 5 years of experience building and shipping production systems across startup, government, nonprofit, and independent environments. I am also studying a master's degree in public administration, where I focus on how technology, institutions, governance, and coordination shape the systems people rely on.

I wanted to reach out because I am very interested in the Senior Full-Stack Engineer role at Limitless. The role description resonated with me because it describes the kind of environment where I do my best work: small teams, high ownership, close collaboration with product, and engineers who design, build, test, ship, and iterate on their own features.

Most of my experience has been in environments where the problem is not fully defined at the beginning. I am used to taking messy workflows, understanding the operating needs behind them, and turning them into software people use. At AVAA, for example, I built SEP, an internal Participant Evaluation System that centralized scholar records, activity tracking, attendance, volunteer hours, and reporting across three chapters. It replaced scattered spreadsheets and gave the team a clearer operating model.

I have also owned full product delivery in startup-like settings. At Free2Z, I led a production migration from React to SvelteKit, improved frontend architecture, connected the product to Python and Django APIs, shipped live video features with Dyte, and built a custom CMS suite. For the U.S. Department of State's Venezuela Affairs Unit, I built Billingua Talent as the sole engineer, from requirements and data model to dashboards, advisor workflows, quality checks, and production delivery.

The product-builder framing at Limitless stood out to me. I like working across frontend and backend, staying close to the user problem, testing my own work, and owning the result after it ships. I care about maintainable code, but I also care about whether the feature solves the product problem. I am comfortable with manual QA, regression checks, release review, and fast iteration based on feedback.

I also use AI-assisted engineering every day. My workflow includes Codex, Claude, Cursor, Gemini, OpenCode, and related tools for planning, debugging, refactoring, implementation, code review, and research. I use them to move faster while staying careful about system behavior and code quality.

The Web3 side of the role is also interesting to me. I have studied and written about Ethernaut, Damn Vulnerable DeFi, Brownie, wallet behavior, flash loans, smart contract security, and blockchain development concepts. I have not worked professionally in prediction markets, but I learn technical domains quickly and enjoy products where engineering details matter.

You can learn more about me here: \href{https://kevinbravo.com/me/ama/}{https://kevinbravo.com/me/ama/}

I would be glad to explore whether there is a fit and how I could help Limitless ship product features end to end while improving quality, speed, and engineering workflow.

Best,

Kevin

\end{document}
