\documentclass[11pt]{article}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{cmap}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage[left=1.15cm,top=1.25cm,right=1.15cm,bottom=0.85cm]{geometry}
\IfFileExists{glyphtounicode.tex}{\input{glyphtounicode}\pdfgentounicode=1}{}
\hypersetup{
    hidelinks,
    pdfauthor={Kevin Bravo},
    pdftitle={Kevin Bravo - Senior Full-Stack Engineer CV},
    pdfsubject={ATS-compliant CV for a Senior Full-Stack Engineer role},
    pdfkeywords={Senior Full-Stack Engineer, Product Engineer, TypeScript, JavaScript, Node.js, React, SvelteKit, Next.js, Full-Stack, Testing, Manual QA, Automated Testing, AI-assisted development, Web3, DeFi}
}
\setlength{\parindent}{0pt}
\hyphenpenalty=10000
\exhyphenpenalty=10000
\emergencystretch=2em
\pagestyle{empty}
\setlist[itemize]{leftmargin=*, noitemsep, topsep=2pt, partopsep=0pt, parsep=2pt, label={\textbf{-}}}

\begin{document}
\raggedright

\begin{center}
    {\LARGE \textbf{Kevin Bravo}}\\
    Senior Full-Stack Engineer | Product Builder, TypeScript \& AI Workflows \\
    \hrulefill
\end{center}

\begin{center}
    Email: \href{mailto:0bravokevin@gmail.com}{0bravokevin@gmail.com}
    | Portfolio: \href{https://kevinbravo.com}{https://kevinbravo.com}
    | GitHub: \href{https://github.com/0bkevin}{https://github.com/0bkevin}
    | LinkedIn: \href{https://www.linkedin.com/in/0bkevin/}{https://www.linkedin.com/in/0bkevin}
    | Location: Remote, Venezuela
\end{center}

\vspace{4pt}
\begin{center}
    \textbf{Professional Summary}
\end{center}
\vspace{-4pt}
Senior software engineer with 5 years of experience designing, building, testing, and shipping production web applications, internal platforms, dashboards, and workflow systems across startup, government, and nonprofit environments. Strong background in TypeScript, JavaScript, Node.js, React, SvelteKit, Next.js, backend integrations, data modeling, API driven product flows, and end to end feature ownership. I work best as a product builder: close to users and product goals, hands-on across frontend and backend, responsible for quality, and comfortable moving quickly with AI assisted workflows while keeping code maintainable.

\vspace{7pt}
\begin{center}
    \textbf{Core Competencies}
\end{center}
\vspace{-4pt}
\textbf{End to end product ownership:} Own discovery, architecture, implementation, manual QA, release quality, production delivery, iteration, and technical support for features and systems. \\
\textbf{Frontend and backend:} TypeScript, JavaScript, Node.js, React, SvelteKit, Next.js, Tailwind CSS, Python, Django, SQL, PostgreSQL, REST APIs, service integrations, dashboards, CMS tooling, SSR, and real-time features. \\
\textbf{Testing and quality:} Manual QA, feature verification, regression checks, acceptance testing, data validation, release review, operational monitoring, and automated testing concepts. \\
\textbf{AI assisted development:} Daily user of Codex, Claude, Cursor, Gemini, OpenCode, T3Code, and related tools for research, prototyping, debugging, code review, and implementation. \\
\textbf{Web3 exposure:} Technical writing and hands-on study around Ethernaut, Damn Vulnerable DeFi, Brownie, wallet behavior, flash loans, smart contract security, Solidity concepts, and blockchain tooling.

\vspace{7pt}
\begin{center}
    \textbf{Work Experience}
\end{center}
\vspace{-4pt}

\textbf{Proyecto Educa} \hfill \textit{Remote, Venezuela} \\
\textbf{Chief Technology Officer} \hfill \textit{Dec 2025 -- Present}
\begin{itemize}
    \item \textbf{Own product and technical direction} for education platforms, translating ambiguous stakeholder needs into product plans, system design, implementation priorities, testing expectations, and shipped software.
    \item \textbf{Lead hands-on execution across the stack} spanning frontend, backend, workflow automation, feature verification, release quality, and system decisions for products used in live operations.
\end{itemize}

\vspace{8pt}
\textbf{Free2Z} \hfill \textit{Remote, Venezuela} \\
\textbf{Principal Software Engineer} \hfill \textit{Apr 2025 -- Apr 2026}
\begin{itemize}
    \item \textbf{Led a production migration from React to SvelteKit}, improving maintainability, frontend architecture, server-side rendering, performance, and delivery speed for a live startup product.
    \item \textbf{Shipped product features end to end} by integrating Python and Django APIs, delivering live video with Dyte, and building a CMS suite for content and operational workflows.
    \item \textbf{Worked across product, implementation, testing, and iteration}, improving user-facing behavior and internal workflows without relying on strict handoffs between teams.
\end{itemize}

\vspace{8pt}
\textbf{U.S. Department of State (via AVAA)} \hfill \textit{Remote, Venezuela} \\
\textbf{Software Engineer | Full-Stack Developer} \hfill \textit{Nov 2024 -- Aug 2025}
\begin{itemize}
    \item \textbf{Built Billingua Talent as the sole engineer}, owning requirements, relational data architecture, backend connected product flows, dashboards, reporting, quality checks, and production delivery.
    \item \textbf{Shipped candidate profiles, advisor dashboards, registration flows, and service-management workflows} that improved talent visibility, English-readiness planning, and operational follow-up across centers.
\end{itemize}

\vspace{8pt}
\textbf{Freelance} \hfill \textit{Remote} \\
\textbf{Software Engineer} \hfill \textit{Sep 2024 -- Dec 2024}
\begin{itemize}
    \item \textbf{Delivered custom web applications, automation scripts, and product solutions} for clients across multiple sectors, owning discovery, prioritization, development, launch, iteration, and support.
\end{itemize}

\vspace{8pt}
\textbf{Asociacion Venezolano Americana de Amistad (AVAA)} \hfill \textit{Remote, Venezuela} \\
\textbf{Software Developer} \hfill \textit{Oct 2022 -- Jul 2024}
\begin{itemize}
    \item \textbf{Built SEP}, a production internal platform that replaced spreadsheet-heavy operations with live scholar records, activity tracking, volunteer-hour logs, attendance workflows, reporting, and chapter-level visibility.
    \item \textbf{Engineered SEA for EducationUSA}, a full-stack operations platform centralizing advisee records, outreach activities, service history, payments, receipts, and institutional alliances.
\end{itemize}

\vspace{8pt}
\textbf{Asociacion Venezolano Americana de Amistad (AVAA)} \hfill \textit{Caracas, Venezuela} \\
\textbf{Software Developer Intern} \hfill \textit{Sep 2021 -- Aug 2022}
\begin{itemize}
    \item \textbf{Built an interactive Power BI dashboard and Python data scripts} that improved analytics workflows, data cleanup, validation, and reporting reliability.
\end{itemize}

\vspace{7pt}
\begin{center}
    \textbf{Projects}
\end{center}
\vspace{-4pt}

\textbf{Billingua Talent} \hfill \textit{Full-Stack Product}
\begin{itemize}
    \item Designed and shipped a professional networking and operations platform combining candidate profiles, advisor workflows, service registration, reporting views, and analytics in one product.
\end{itemize}

\vspace{6pt}
\textbf{AI-Assisted Engineering Workflow} \hfill \textit{Ongoing}
\begin{itemize}
    \item Use AI coding tools daily to accelerate product research, prototyping, debugging, implementation, refactoring, and code review while preserving engineering judgment and maintainability.
\end{itemize}

\vspace{6pt}
\textbf{Web3 and DeFi Technical Writing} \hfill \textit{Independent}
\begin{itemize}
    \item Published technical walkthroughs on Ethernaut, Damn Vulnerable DeFi, Brownie, wallet behavior, flash loans, smart contract security, and blockchain development concepts.
\end{itemize}

\vspace{7pt}
\begin{center}
    \textbf{Leadership}
\end{center}
\vspace{-4pt}
\textbf{Dev3pack:} Organized the Caracas hub for a global Web3 and AI hackathon, coordinating logistics, sponsors, speakers, mentors, and participant support. \\
\textbf{JA Venezuela Alumni:} Vice President supporting strategy, partnerships, operations, and institutional growth for a national alumni network. \\
\textbf{Technovation Girls Venezuela:} Code mentor guiding students through research, prototyping, technical troubleshooting, and mobile app development.

\vspace{7pt}
\begin{center}
    \textbf{Education}
\end{center}
\vspace{-4pt}
\textbf{Instituto de Estudios Superiores de Administracion (IESA)} \hfill \textit{Caracas, Venezuela} \\
Master of Public Administration \hfill \textit{In Progress}

\vspace{7pt}
\begin{center}
    \textbf{Skills}
\end{center}
\vspace{-4pt}
\textbf{Technical:} TypeScript, JavaScript, Node.js, React, SvelteKit, Next.js, Python, Django, SQL, PostgreSQL, REST APIs, Tailwind CSS, Docker, Power BI, HTML, CSS, data modeling, backend workflows, API integrations, dashboards, internal tools, CMS tooling, SSR, real-time features, workflow automation, AI-assisted development. \\
\textbf{Quality and Delivery:} manual QA, feature verification, regression checks, acceptance testing, automated testing concepts, release ownership, production iteration, maintainable code, debugging, stakeholder feedback loops. \\
\textbf{Professional:} product mindset, independent feature ownership, technical leadership, startup execution, cross functional collaboration, user centered problem solving, operating in ambiguity, moving fast while maintaining quality. \\
\textbf{Languages:} Spanish (Native), English (C1).

\end{document}
