\documentclass[11pt]{article}
\usepackage{hyperref}
\usepackage{cmap}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage[left=1.5cm,top=1.6cm,right=1.5cm,bottom=1.5cm]{geometry}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0.7em}

\begin{document}

\begin{center}
    {\LARGE \textbf{Kevin Bravo}}\\
    Software Engineer | Backend, AI Infrastructure \& Full-Stack Systems \\
    \href{mailto:0bravokevin@gmail.com}{0bravokevin@gmail.com} \textbullet\ 
    \href{http://www.kevinbravo.com}{www.kevinbravo.com}
\end{center}

\vspace{0.5em}

June 4, 2026

Paradex Hiring Team,

I am excited to apply to Paradex because the role aligns closely with the kind of engineering work I want to do. I am drawn to products that demand strong backend systems, careful technical judgment, and a high level of ownership. Paradex brings those elements together in a space I have been following closely for several years.

Most of my career has followed the same pattern. A team has a messy process, weak tooling, or a product that does not yet exist. I turn that into software people can rely on. For the last 5 years, I have built production systems for the U.S. Department of State's Venezuela Affairs Unit, Free2Z, and AVAA. My work has covered backend architecture, full-stack product development, data modeling, API integrations, internal tools, and reporting systems.

At Free2Z, I led a production migration from React to SvelteKit, redesigned core architecture, integrated a Python and Django API, and shipped live product features. For the U.S. Department of State's Venezuela Affairs Unit, I built Billingua Talent as the sole engineer and owned the product from data model to production delivery. At AVAA, I built operational platforms that replaced spreadsheet-heavy processes with live systems for tracking, reporting, and daily decisions. I am comfortable owning the whole path from structure to implementation.

I have been in the blockchain space since late 2021 through personal projects, technical study, and hands-on development. I have worked with Solidity, Rust, and Cairo. I am especially interested in zero-knowledge systems, blockchain interoperability, and distributed systems. Crypto kept my attention because it forces precision. Systems fail in public. Assumptions get tested fast. The engineering bar is higher, and that is exactly the pull for me.

I also use modern AI tooling heavily in my workflow for research, prototyping, debugging, and technical exploration. It helps me move faster and test more ideas, but I still rely on first-principles thinking and careful implementation.

Paradex appeals to me for a simple reason. It expects engineers to own their work, think clearly, and ship. That is the environment where I am most useful.

I would be glad to discuss how my background in backend systems, full-stack delivery, and blockchain-focused personal work could contribute to Paradex.

Sincerely,

Kevin Bravo

\end{document}
