\documentclass[11pt]{article}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{cmap}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage[left=1.06cm,top=1.7cm,right=1.06cm,bottom=0.6cm]{geometry}
\setlength{\parindent}{0pt}
\setlist[itemize]{leftmargin=*, noitemsep, topsep=0pt, partopsep=0pt, parsep=0pt}

\begin{document}
\begin{center}
    {\LARGE \textbf{Kevin Bravo}}\\
    Software Engineer | Tauri, React, Flutter, TypeScript \\
    \hrulefill
\end{center}

\begin{center}
    \href{mailto:0bravokevin@gmail.com}{0bravokevin@gmail.com} \textbullet\ \href{http://www.kevinbravo.com}{www.kevinbravo.com} \textbullet\ Remote, Venezuela
\end{center}

\vspace{2pt}

\textbf{Profile}\\
Software engineer focused on shipping production software across frontend, backend, and product architecture. I have built and maintained React and TypeScript applications end to end, and I have recent hands-on experience contributing to Tauri desktop development and building mobile applications with Flutter. My work consistently centers on turning ambiguous operating needs into reliable user-facing products, with strong attention to system design, API integrations, data modeling, testing, and release quality.

\begin{center}
    \textbf{Experience}
\end{center}

\textbf{Proyecto Educa} \hfill Remote, Venezuela \\
\textbf{Chief Technology Officer} \hfill Dec 2025 -- Present
\begin{itemize}
    \item Direct product and technical roadmap across frontend, backend, testing, delivery, and release quality for education platforms used in live operations.
    \item Own architecture decisions, implementation planning, and execution across user-facing features, internal systems, and platform reliability.
\end{itemize}

\vspace{10pt}

\textbf{Free2Z} \hfill Remote, Venezuela \\
\textbf{Principal Software Engineer} \hfill Apr 2025 -- Apr 2026
\begin{itemize}
    \item Led a production frontend migration from React to SvelteKit, improving maintainability, performance, server-side rendering, and cross-platform behavior.
    \item Integrated frontend systems with Python and Django APIs, shipped real-time video features, and built CMS workflows for content and product operations.
\end{itemize}

\vspace{10pt}

\textbf{U.S. Department of State (via AVAA)} \hfill Remote, Venezuela \\
\textbf{Software Engineer | Full-Stack Developer} \hfill Nov 2024 -- Aug 2025
\begin{itemize}
    \item Built Billingua Talent as sole engineer, owning architecture, relational data modeling, implementation, and production delivery.
    \item Shipped dashboards, service-management workflows, candidate profiles, registrations, and reporting systems that replaced fragmented manual operations.
\end{itemize}

\vspace{10pt}

\textbf{Freelance} \hfill Remote \\
\textbf{Software Engineer} \hfill Sep 2024 -- Dec 2024
\begin{itemize}
    \item Delivered custom product builds across frontend, backend, automation, and data workflows for clients with varied operational requirements.
    \item Owned discovery, prioritization, development, testing, launch, iteration, and technical support across the full product lifecycle.
\end{itemize}

\vspace{10pt}

\textbf{Asociacion Venezolano Americana de Amistad (AVAA)} \hfill Remote, Venezuela \\
\textbf{Software Developer} \hfill Oct 2022 -- Jul 2024
\begin{itemize}
    \item Built operational platforms for scholar records, attendance, volunteer hours, paid services, receipts, outreach, and reporting across multiple chapters.
    \item Replaced spreadsheet-heavy processes with live systems used for daily coordination, service tracking, and decision-making.
\end{itemize}

\begin{center}
    \textbf{Selected Projects}
\end{center}

\textbf{Orpan} \hfill Tauri, React, Tailwind CSS, SQLite \\
\textbf{Desktop Application Contributor}
\begin{itemize}
    \item Contributed to the development of a precision language-acceleration desktop application packaged with Tauri.
    \item Helped deliver a React and Tailwind interface backed by a Tauri runtime, embedded SQLite, premium on-device text-to-speech, and deterministic offline study pipelines.
    \item Worked on a local-first desktop experience where curated bilingual corpora become an interactive study environment without depending on constant connectivity.
\end{itemize}

\vspace{10pt}

\textbf{Knowfi} \hfill Flutter, Dart \\
\textbf{Mobile Application Builder}
\begin{itemize}
    \item Built a Flutter mobile application for personal finance management focused on helping users organize and understand day-to-day financial activity.
    \item Designed and implemented the product as a mobile-first experience, strengthening my experience with cross-platform UI development and state-driven application flows.
\end{itemize}

\vspace{10pt}

\textbf{Independent Projects} \hfill Remote \\
\textbf{Product Engineering}
\begin{itemize}
    \item Built Brio, a mobile-first control plane for an AI agent system focused on pairing, session control, relay routing, logs, and operational visibility.
    \item Publish technical walkthroughs covering software security, protocol behavior, and implementation analysis.
\end{itemize}

\begin{center}
    \textbf{Education}
\end{center}

\textbf{Instituto de Estudios Superiores de Administracion (IESA)} \hfill Caracas, Venezuela \\
Master of Public Administration \hfill In Progress

\begin{center}
    \textbf{Skills}
\end{center}

\textbf{Desktop and Mobile:} Tauri, Flutter, cross-platform application development, mobile-first UX, desktop packaging, local-first application flows

\textbf{Frontend:} TypeScript, JavaScript, React, Svelte, SvelteKit, Next.js, Tailwind CSS, responsive UI development

\textbf{Backend and Data:} Python, Django, SQL, PostgreSQL, SQLite, REST APIs, relational data modeling, workflow automation

\textbf{Systems:} real-time features, offline-oriented product design, CMS tooling, dashboard development, testing, release ownership

\textbf{Language:} Spanish (Native), English (C1)

\end{document}
