\documentclass[10pt]{article}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{cmap}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage[left=0.95cm,top=0.92cm,right=0.95cm,bottom=0.55cm]{geometry}
\IfFileExists{glyphtounicode.tex}{\input{glyphtounicode}\pdfgentounicode=1}{}
\hypersetup{
    hidelinks,
    pdfauthor={Kevin Bravo},
    pdftitle={Kevin Bravo - Runlayer Founding Support Engineer CV},
    pdfsubject={ATS-compliant CV for Founding Support Engineer role at Runlayer},
    pdfkeywords={Founding Support Engineer, Technical Support Engineer, Solutions Engineer, Customer-facing Engineering, SaaS, Developer Tools, AI Agents, MCP, Model Context Protocol, OAuth, SSO, SCIM, Kubernetes, EKS, ECS, Helm, Terraform, AWS, Azure, GCP, PostgreSQL, Python, TypeScript, HTTP debugging, runbooks, knowledge base, Pylon, Slack, Teams, observability, connectors, deployments}
}
\setlength{\parindent}{0pt}
\hyphenpenalty=10000
\exhyphenpenalty=10000
\emergencystretch=2em
\pagestyle{empty}
\setlist[itemize]{leftmargin=*, noitemsep, topsep=0pt, partopsep=0pt, parsep=0pt, label={\textbf{-}}}

\begin{document}
\raggedright

\begin{center}
    {\LARGE \textbf{Kevin Bravo}}\\
    Founding Support Engineer | AI Agents, Infrastructure Support \& Developer Tools \\
    \hrulefill
\end{center}

\begin{center}
    Email: \href{mailto:0bravokevin@gmail.com}{0bravokevin@gmail.com}
    | Portfolio: \href{https://kevinbravo.com}{https://kevinbravo.com}
    | GitHub: \href{https://github.com/0bkevin}{https://github.com/0bkevin}
    | LinkedIn: \href{https://www.linkedin.com/in/0bkevin/}{https://www.linkedin.com/in/0bkevin}
    | Location: Remote, Venezuela
\end{center}

\vspace{2pt}
\begin{center}
    \textbf{Professional Summary}
\end{center}
\vspace{-6pt}
Software engineer with 5 years of experience building, deploying, maintaining, and supporting production systems, internal platforms, dashboards, APIs, data workflows, and AI-agent tooling. Strong fit for founding technical support roles that need customer-facing debugging, clear written communication, runbooks, escalation discipline, and hands-on work across TypeScript, Python, PostgreSQL, HTTP requests, cloud deployments, and AI-native workflows.

\vspace{3pt}
\begin{center}
    \textbf{Runlayer Role Fit}
\end{center}
\vspace{-6pt}
\textbf{Support and triage:} Production debugging, issue reproduction, stakeholder support, technical troubleshooting, manual QA, regression checks, runbook-style documentation, customer-facing explanations, and recurring ticket elimination. \\
\textbf{Infrastructure and integrations:} Azure deployments, Azure VPS, Cloudflare Pages/Workers, Turnstile verification, AWS/Azure/GCP model API usage, Docker, environment variables, logs, service integrations, PostgreSQL, SQL, TypeScript, Python, Django, REST APIs, and HTTP debugging. \\
\textbf{AI and enterprise support domains:} Codex, Claude, Cursor, Gemini, OpenCode, T3Code, MCP concepts, AI agents, OAuth concepts, SSO/SCIM fundamentals, connector activation, policy configuration, Kubernetes pod logs, EKS/ECS, Helm, Terraform, CloudWatch, VPCs, Pylon, Slack, and Teams.

\vspace{3pt}
\begin{center}
    \textbf{Work Experience}
\end{center}
\vspace{-6pt}

\textbf{Proyecto Educa} \hfill \textit{Remote, Venezuela} \\
\textbf{Chief Technology Officer} \hfill \textit{Dec 2025 - Present}
\begin{itemize}
    \item \textbf{Own product and technical direction} for education platforms, translating stakeholder needs into architecture, support workflows, implementation priorities, testing expectations, production issue handling, and shipped software.
\end{itemize}

\vspace{2pt}
\textbf{Free2Z} \hfill \textit{Remote, Venezuela} \\
\textbf{Principal Software Engineer} \hfill \textit{Apr 2025 - Apr 2026}
\begin{itemize}
    \item \textbf{Led a production migration from React to SvelteKit}, improving architecture, SSR, maintainability, performance, state handling, and production behavior for a live startup platform.
    \item \textbf{Debugged and shipped backend-connected workflows} by integrating Python/Django APIs, Dyte live video, CMS tooling, Markdown publishing, and operational features.
\end{itemize}

\vspace{2pt}
\textbf{U.S. Department of State (via AVAA)} \hfill \textit{Remote, Venezuela} \\
\textbf{Software Engineer | Full-Stack Developer} \hfill \textit{Nov 2024 - Aug 2025}
\begin{itemize}
    \item \textbf{Built and supported Billingua Talent as the sole engineer}, owning requirements, relational data architecture, backend-connected flows, dashboards, reporting, quality checks, deployment, and maintenance.
    \item \textbf{Supported advisors and program operators} by turning feedback and recurring questions into clearer workflows, reporting views, data fixes, and reliable service-management flows.
\end{itemize}

\vspace{2pt}
\textbf{Asociacion Venezolano Americana de Amistad (AVAA)} \hfill \textit{Remote, Venezuela} \\
\textbf{Software Developer} \hfill \textit{Oct 2022 - Jul 2024}
\begin{itemize}
    \item \textbf{Built, deployed, and maintained SEP and SEA on Azure}, replacing spreadsheet operations with internal platforms for scholar records, attendance, volunteer hours, advisee histories, payments, services, and reports.
    \item \textbf{Served as technical owner for internal users}, handling issue reports, data cleanup, user support, workflow changes, reporting reliability, and Python scripts for analytics and validation.
\end{itemize}

\vspace{3pt}
\begin{center}
    \textbf{Selected Projects}
\end{center}
\vspace{-6pt}

\textbf{Hermes, Zrode, and Brio} \hfill \textit{AI Agents, Developer Tooling, Azure VPS}
\begin{itemize}
    \item \textbf{Run Hermes as a personal AI agent on an Azure VPS}, maintaining server configuration, environment variables, remote access, uptime, logs, and daily operational use.
    \item \textbf{Build Zrode and Brio for agentic engineering workflows}: Zrode is an agentic development environment; Brio is a mobile-first control plane for Hermes with session control, relay routing, logs, and operational visibility.
\end{itemize}

\vspace{2pt}
\textbf{Cloudflare Portfolio Support Flow} \hfill \textit{TypeScript, Astro, Cloudflare}
\begin{itemize}
    \item \textbf{Implemented a TypeScript API route with Cloudflare Turnstile verification}, Pages/Workers environment bindings, request validation, JSON responses, email integration, and error handling.
\end{itemize}

\vspace{3pt}
\begin{center}
    \textbf{Education, Leadership, and Skills}
\end{center}
\vspace{-6pt}
\textbf{IESA:} Master of Public Administration, in progress. \textbf{Leadership:} Dev3pack Caracas hub organizer, JA Venezuela Alumni Vice President, Technovation Girls Venezuela code mentor. \\
\textbf{Technical:} TypeScript, JavaScript, Python, Django, SQL, PostgreSQL, SQLite, REST APIs, HTTP debugging, data modeling, dashboards, Power BI, Docker, Azure, Azure VPS, Cloudflare, AWS, GCP, model APIs, logs, environment configuration, release support, AI-assisted development, MCP concepts, agent tooling. \\
\textbf{Languages:} Spanish (Native), English (C1).

\end{document}
