\documentclass[10pt]{article}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{cmap}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage[left=0.9cm,top=0.78cm,right=0.9cm,bottom=0.48cm]{geometry}
\IfFileExists{glyphtounicode.tex}{\input{glyphtounicode}\pdfgentounicode=1}{}
\hypersetup{
    hidelinks,
    pdfauthor={Kevin Bravo},
    pdftitle={Kevin Bravo - Integration Engineer Backend CV},
    pdfsubject={ATS-compliant CV for Integration Engineer role focused on backend systems, healthcare integrations, Node.js, Python, PostgreSQL, MongoDB, reliability, and production ownership},
    pdfkeywords={Kevin Bravo, Integration Engineer, Backend Engineer, Backend Engineering, Node.js, Python, TypeScript, PostgreSQL, MongoDB, queues, async patterns, error handling, observability, production ownership, runbooks, incident response, healthcare infrastructure, EHR integrations, APIs, REST APIs, Django, SQL, Azure, Docker, cloud, AI infrastructure, Spanish native, Latin America}
}
\setlength{\parindent}{0pt}
\hyphenpenalty=10000
\exhyphenpenalty=10000
\emergencystretch=2em
\pagestyle{empty}
\setlist[itemize]{leftmargin=*, noitemsep, topsep=0pt, partopsep=0pt, parsep=0pt, label={\textbf{-}}}

\begin{document}
\raggedright

\begin{center}
    {\LARGE \textbf{Kevin Bravo}}\\
    Integration Engineer | Backend Systems, APIs \& Production Ownership \\
    \hrulefill
\end{center}

\begin{center}
    Email: \href{mailto:0bravokevin@gmail.com}{0bravokevin@gmail.com}
    | Portfolio: \href{https://kevinbravo.com}{https://kevinbravo.com}
    | GitHub: \href{https://github.com/0bkevin}{https://github.com/0bkevin}
    | LinkedIn: \href{https://www.linkedin.com/in/0bkevin/}{https://www.linkedin.com/in/0bkevin}
    | Location: Remote, Latin America
\end{center}
\fontsize{9.35}{10.35}\selectfont

\vspace{1pt}
\begin{center}
    \textbf{Professional Summary}
\end{center}
\vspace{-7pt}
Software engineer with 5 years of experience building, deploying, maintaining, and supporting production backend and full-stack systems across startup, government, nonprofit, and freelance environments. Strong background in backend integrations, APIs, PostgreSQL/SQL, Python, Django, TypeScript/Node.js web tooling, production debugging, stakeholder support, and converting undocumented workflows into reliable internal platforms. Native Spanish speaker, English C1, with a healthcare-adjacent academic background in Occupational Therapy.

\vspace{3pt}
\begin{center}
    \textbf{Backend and Integration Skills}
\end{center}
\vspace{-7pt}
\textbf{Backend engineering:} Python, Django, TypeScript, JavaScript, Node.js ecosystem, REST APIs, API routes, service integrations, request validation, async workflows, queues, error handling, idempotency, data validation, and backend-connected product flows. \\
\textbf{Data systems:} PostgreSQL, SQL, SQLite, MongoDB and document-database fundamentals, relational schema design, query design, query optimization, reporting models, migrations, analytics workflows, and data cleanup. \\
\textbf{Reliability and operations:} Azure deployments, Azure VPS operations, Cloudflare Pages/Workers, Docker, logs, observability practices, production debugging, incident follow-up, runbook-style documentation, manual QA, regression checks, Git, code reviews, CI/CD concepts, and environment configuration. \\
\textbf{Domain fit:} Integration system design, first-principles system mapping, ambiguous requirements, direct written communication, Spanish-native stakeholder support, AI-assisted engineering, open-source research, healthcare workflow awareness, and clinical-record sensitivity.

\vspace{3pt}
\begin{center}
    \textbf{Work Experience}
\end{center}
\vspace{-7pt}

\textbf{Proyecto Educa} \hfill \textit{Remote, Venezuela} \\
\textbf{Chief Technology Officer} \hfill \textit{Dec 2025 - Present}
\begin{itemize}
    \item \textbf{Own product and technical direction} for education platforms, translating ambiguous stakeholder needs into architecture, backend data workflows, testing expectations, release quality, and support processes.
\end{itemize}

\vspace{2pt}
\textbf{Free2Z} \hfill \textit{Remote, Venezuela} \\
\textbf{Principal Software Engineer} \hfill \textit{Apr 2025 - Apr 2026}
\begin{itemize}
    \item \textbf{Shipped backend-connected product features} by integrating Python and Django APIs with frontend workflows, delivering Dyte live-video functionality, and building CMS tooling for operational publishing.
    \item \textbf{Led a production migration from React to SvelteKit}, improving architecture, SSR behavior, maintainability, performance, state handling, and reliability for a live startup platform.
\end{itemize}

\vspace{2pt}
\textbf{U.S. Department of State (via AVAA)} \hfill \textit{Remote, Venezuela} \\
\textbf{Software Engineer | Full-Stack Developer} \hfill \textit{Nov 2024 - Aug 2025}
\begin{itemize}
    \item \textbf{Built and supported Billingua Talent as the sole engineer}, owning requirements, relational data architecture, backend-connected flows, dashboards, reporting, quality checks, deployment, and maintenance.
    \item \textbf{Mapped an undocumented operational workflow into a production platform}, giving advisors tools for candidate profiles, English-readiness tracking, service registration, analytics, multi-center follow-up, and issue resolution.
\end{itemize}

\vspace{2pt}
\textbf{Asociacion Venezolano Americana de Amistad (AVAA)} \hfill \textit{Remote, Venezuela} \\
\textbf{Software Developer} \hfill \textit{Oct 2022 - Jul 2024}
\begin{itemize}
    \item \textbf{Built, deployed, and maintained SEP on Azure}, replacing spreadsheet-heavy operations with live scholar records, activity tracking, volunteer-hour logs, attendance workflows, reporting, and visibility across 3 national chapters.
    \item \textbf{Engineered SEA for EducationUSA}, centralizing advisee records, outreach activities, service history, payments, receipts, institutional alliances, and reporting into a backend-driven operations platform.
    \item \textbf{Served as technical owner for internal users}, handling issue reports, user support, data cleanup, workflow changes, reporting reliability, and Python scripts for analytics and validation.
\end{itemize}

\vspace{3pt}
\begin{center}
    \textbf{Selected Technical Fit}
\end{center}
\vspace{-7pt}
\textbf{Integration ownership:} Built systems that became the source of truth for records, payments, attendance, services, reporting, advisor workflows, and stakeholder dashboards. \\
\textbf{Backend reliability:} Practical experience with request validation, data validation, error handling, logs, production debugging, manual and regression testing, deployment ownership, and user-facing incident follow-up. \\
\textbf{AI and tooling:} Daily AI-assisted workflow with Codex, Claude, Cursor, Gemini, and OpenCode. Run Hermes as a personal AI agent on an Azure VPS; build Zrode for agentic development and Brio as a mobile-first control plane with session control, relay routing, logs, and operational visibility. \\
\textbf{Open-source habits:} Maintains public GitHub projects, reads documentation and source code to debug behavior, and builds on Django, SvelteKit, Astro, and TypeScript ecosystem tooling.

\vspace{3pt}
\begin{center}
    \textbf{Education and Languages}
\end{center}
\vspace{-7pt}
\textbf{Instituto de Estudios Superiores de Administracion (IESA):} Master of Public Administration, in progress. \\
\textbf{Universidad Central de Venezuela:} Occupational Therapy, Cum Laude, 2023. \\
\textbf{Languages:} Spanish (Native), English (C1).

\end{document}
